### 2017-11-05 bingol-LaTeX-Template-Paper/Bingol-Template-Paper.tex
bingol-LaTeX-Template-Paper commited.

% !TEX spellcheck = en_US

%\documentclass[pre,twocolumn,showkeys,longbibliography,nofootinbib]{revtex4-1}
\documentclass[pre,twocolumn,showkeys,longbibliography]{revtex4-1}
%\documentclass[twocolumn,preprintnumbers,amsmath,amssymb,superscriptaddress,pre]{revtex4}

%: ==== HB Header Common Packages v20160423 ====V
	\usepackage[utf8]{inputenc} % To use Unicode characters
	\usepackage[iso]{datetime}
	%	\usepackage{etex}

	\usepackage[a4paper]{geometry}

	\usepackage{xcolor}
	% black, blue, brown, cyan, darkgray, gray, green, lightgray, lime, 
	% magenta, olive, orange, pink, purple, red, teal, violet, white, yellow
	\usepackage[colorlinks=true,linkcolor=red,urlcolor=blue,citecolor=red]%
		{hyperref}
	\usepackage{graphicx,epstopdf}
	% \graphicspath{{fig}}
	\graphicspath{{../common/figures/}}
	% \DeclareGraphicsExtensions{.pdf,.jpeg,.png,.eps}
	% \DeclareGraphicsRule{.tif}{png}{.png}%
	%	{`convert #1 `dirname #1`/`basename #1 .tif`.png}
%	\usepackage{subfigure}
%\usepackage{subfig}
\usepackage{subcaption}

%: ==== HB Header Common Declarations v20170816 ====V
	\newcommand{\hbTimeStamp}{{\color{red}--Draft-- v\today/\currenttime}} % version
	%
	\newcommand{\reffig}[1]{Fig.~\ref{#1}}
	\newcommand{\refeq}[1]{Eq.~\ref{#1}}
	\newcommand{\reftbl}[1]{Table~\ref{#1}}
	\newcommand{\refsec}[1]{Sec.~\ref{#1}}
	\newcommand{\refcite}[1]{Ref~\cite{#1}}
	\newcommand{\refalg}[1]{Algorithm~\cite{#1}}
	\newcommand{\reflst}[1]{List.~\ref{#1}}  % code listing
	%
	\newcommand{\refthm}[1]{Theorem~\ref{#1}}
	\newcommand{\refthmA}[2]{\refthm{#1}(\ref{#2}}
	\newcommand{\reflem}[1]{Lemma~\ref{#1}}
	\newcommand{\refdef}[1]{Definition~\ref{#1}}
	\newcommand{\refexmp}[1]{Example~\ref{#1}}
	%
	\newcommand{\hbQuote}[1]{{\small \textsf{``#1''}}}
	%
	\newcommand{\hbCode}[1]{\texttt{#1}}
	%
	\newcommand{\hbIdea}[1]{{\color{olive}{\scriptsize [{#1}]}}}
	\newcommand{\hbFootnote}[2]{\footnote{{\color{red} @#1 : }#2}}
% ==== HB Header Common Declarations ====A

%: ==== HB Header Common Math v20170530 ====V
	% ams
	\usepackage{amsmath, amssymb,amsfonts,amsthm}

	\newcommand{\hbVec}[1]{\mathbf{#1}}	% vector
	\newcommand{\hbAbs}[1]{| #1 |}	% absolute value
	\newcommand{\hbNorm}[1]{\left\lVert #1 \right\rVert}	% norm 2
	\newcommand{\hbMat}[1]{\mathbf{#1}}	% matrix
	\newcommand{\hbSet}[1]{\mathcal{#1}}	%
	\newcommand{\argmin}[2]{\underset{#1}{\operatorname{arg \, min}}\;#2}
	\newcommand{\argmax}[2]{\underset{#1}{\operatorname{arg \, max}}\;#2}

	\theoremstyle{plain}% default
	\newtheorem{thm}{Theorem}[section]
	\newtheorem{lem}[thm]{Lemma}
	\newtheorem{prop}[thm]{Proposition}
	\newtheorem*{cor}{Corollary}
	\theoremstyle{definition}
	\newtheorem{defn}{Definition}[section]
	\newtheorem{conj}{Conjecture}[section]
	\newtheorem{exmp}{Example}[section]
	\theoremstyle{remark}
	\newtheorem*{rem}{Remark}
	\newtheorem*{note}{Note}
% ==== HB Header Common Math v20170530 ====A

%: == HB Code Listing v20161002 ====V
\usepackage{listingsutf8}
%\usepackage{listings}             % Include the listings-package
\definecolor{hbGreen}{rgb}{0,0.6,0}
\definecolor{hbGray}{rgb}{0.5,0.5,0.5}
\definecolor{hbMauve}{rgb}{0.58,0,0.82}
\definecolor{hbbgColor}{rgb}{0.98,0.98,0.98}
%
\lstset{ %
	backgroundcolor=\color{hbbgColor},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}
%  basicstyle=\tiny, % the size of the fonts that are used for the code
	basicstyle=\tiny\ttfamily, % the size of the fonts that are used for the code
%  basicstyle=\scriptsize\ttfamily, % the size of the fonts that are used for the code
%  basicstyle=\footnotesize\ttfamily, % the size of the fonts that are used for the code
	breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
	breaklines=true,                 % sets automatic line breaking
	captionpos=b,                    % sets the caption-position to bottom
	commentstyle=\color{hbGreen},    % comment style
	deletekeywords={...},            % if you want to delete keywords from the given language
	escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
	extendedchars=true,              % lets you use non-ASCII characters; for 8-bits encodings only, does not work with UTF-8
	frame=single,                    % adds a frame around the code
	keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
	keywordstyle=\color{blue},       % keyword style
	language=Sh,                     % the language of the code
	morekeywords={*,...},            % if you want to add more keywords to the set
	numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
	numbersep=5pt,                   % how far the line-numbers are from the code
	numberstyle=\tiny\color{hbGray}, % the style that is used for the line-numbers
	rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
	showspaces=false,                % show spaces everywhere adding particular underscores; it overrides 'showstringspaces'
	showstringspaces=false,          % underline spaces within strings only
	showtabs=false,                  % show tabs within strings adding particular underscores
	stepnumber=2,                    % the step between two line-numbers. If it's 1, each line will be numbered
	stringstyle=\color{hbMauve},     % string literal style
	tabsize=1,                       % sets default tabsize to 2 spaces
	title=\lstname                   % show the filename of files included with \lstinputlisting; also try caption instead of title
	literate={├}{|}1 {─}{--}1 {└}{+}1
}
\lstset{basicstyle=\ttfamily}
% == HB Code Listing v20161002 ====A

%: ==== HB Track Changes v20170522 ====V
	\usepackage{changes}
	% black, blue, brown, cyan, darkgray, gray, green, lightgray, lime, 
	% magenta, olive, orange, pink, purple, red, teal, violet, white, yellow

	\definechangesauthor[name=Haluk Bingol,color=purple]{hb}
	\definechangesauthor[name=Aaaa Bbbb,color=blue]{ab}
	\setremarkmarkup{(#2)}

	%\listofchanges    % track changes use at the bottom

	% ==== usage

	%\added[id=hb]{
	%	aaa
	%}

	%\replaced[id=hb]{
	%	aaa
	%}{
	%	bob
	%}

	%\deleted[id=hb]{
	%	aaa
	%}

	%\added[id=hb]{newText}
	%\added[id=hb,remark={yourRemark}]{newText}
	%\deleted[id=hb]{deletedText}
	%\deleted[id=hb,remark=yourRemark]{deletedText}
	%\replaced[id=hb]{newText}{deletedText}
%  ==== HB Track Changes v20170522 ====V

%: ======= specific ===============
% frequently used terms
\newcommand{\hbDTex}{\hbCode{.tex}}
\newcommand{\hbDPdf}{\hbCode{.pdf}}
\newcommand{\hbSSpecific}{\hbCode{specific}}

\DeclareGraphicsExtensions{.png}
%
\DeclareMathOperator{\sgn}{sgn}
\DeclareMathOperator{\cov}{cov}
%
%\newcommand{\hbAvg}[1]{\widehat{#1}}
\newcommand{\hbOpt}[1]{{#1}^*}

\newcommand{\hSoX}{\mathbb{X}} % generic set
\newcommand{\hSoN}{\mathbb{N}} % the set of natural numbers
\newcommand{\hSoR}{\mathbb{R}} % the set of real numbers

% ======= specific ===============

%\usepackage{lineno,hyperref}
%\modulolinenumbers[5]

%\usepackage{lineno}
%\usepackage[switch,columnwise]{lineno}
\RequirePackage{lineno}
%\linenumbers

% ========================================
\begin{document}

%\setpagewiselinenumbers
%\modulolinenumbers[5]
%\linenumbers

\title{
	My \LaTeX\ Paper Template 
}
\author{Haluk O. Bingol}

\affiliation{
	Deptment of Computer Engineering,\\
	Bogazici University\\
	Istanbul, Turkey\\
	bingol@boun.edu.tr
}
%\date{\today}
\date{\hbTimeStamp}

\begin{abstract}
	This is my \LaTeX\ template for paper.
\end{abstract}

% ========================================
\keywords{
	LateX paper template;
	keywordB;
	keywordC;
}

% ========================================
\maketitle
\tableofcontents

%\linenumbers

% ========================================
\section{Introduction}

This is my paper template. 
It is developed by experience, necessities, best practices.

% =======================================
\section{\LaTeX\ source code conventions}

Consider \LaTeX\ code as programming language code. 
Actually it is a programming language.

% =======================================
\subsection{left start}

Start your line at the left most position.
Do not indent paragraphs unless they are nested within a structure such as \verb!begin-end! block.
So indentation should be used properly.

% =======================================
\subsection{Keep the line length short}

Some editors organize one paragraph of \LaTeX\ code as one line.
Try not to use such an editors.
The lines should be short.
There are two advantages for shorter lines.
\begin{enumerate}

	\item
	\LaTeX\ works on line.
	Any error message it produces provide you a line number. 
	If the line is a long one,
	it is harder to locate the error.

	\item
	Many version control system such as git works on line as prime object.
	Any change in a line is tracked.
	If the line is too long,
	tracking gets more space since entire line has to be considered.

\end{enumerate}
If line gets too long,
divide it by a ``return'' at a proper point.
A possible places to break the line are ``that'', ``where'', ``which'' phrases or ``else'' part of ``if''.

% =======================================
\subsection{Usage of space and indentation}

Use space and indentation freely so that your source code would be easy to read and maintain.
For example use 4 empty line and followed by a comment before section separators.
See the source code of this paragraph.
See also the source code of the previous ``enumerate'' block.

In math mode, 
use spaces to increase readablility.
For example, see the source code of this in line math equation.
This is binomial number
$
	a = {n \choose r}
$
with smart usage of spaces.
The similar smart space usage can be seen in this math display format, too.
\begin{align}
	\bar{a} 
		= 
			\frac{1}{\hbAbs{A}}
			\sum_{i \in A} a_{i}
		= 5.
\end{align}

Using math and not math mode.
If you are talking about a variable,
use math mode such as $a$.
Any numeric value is recommended to be in math mode.
Notice that -1 in text mode is quite different than $-1$ in math mode.
Use $k$-means, rather than $k-$means.

% =======================================
\section{Header Part}

Note that timestamp \hbTimeStamp\ that helps to keep track of versions while the paper is developed.
Do not forget to remove it before submission.

% =======================================
\subsection{TexShop Specific}

I use TexShop.
It has some features that I use.
\begin{itemize}

	\item
	Tag list feature of TeXShop enables you to directly go to a segment of your document.
	Sections are automatically listed in here.
	I need to extend that for my purposes.
	A \LaTeX\  comment starts with ``\hbCode{\%}''.
	If comment starts with`` \hbCode{\%:}'',
	note the additional ``\hbCode{:}'',
	then it is listed in the tags list, too.
	I use this feature to fast access to some parts of the document such as figures and tables.
	So I add comments such as 
	``\hbCode{\%: -fig.1}'' for figure 1 and
	``\hbCode{\%: -tbl 3}'' for table 3.

	\item 
	\hbCode{\% !TEX spellcheck = en\_US} forces the spellchecker to use American English.

\end{itemize}

% =======================================
\subsection{Common Packages}

% =======================================
\subsection{Common Declarations}

% =======================================
\subsection{Specific}

Anything that is specific to this paper should be defined in \hbSSpecific\ in the header.

% =======================================
\section{Multi-Author Case}

Usually more than one author involved.
They have to keep track of changes, leave messages to each other
while the paper developes.

Suppose we have two authors, namely HB and AB.
Note that you need to modify 
\hbCode{definechangesauthor}
in 
\hbCode{changes} package.
You may want to set different colors, too.

% =======================================
\subsection{Track Changes}

Authors should be able to add, delete and change parts of the document.
\deleted[id=hb]{
	HB removes this part.
}
\added[id=ab]{
	AB adds this part.
}
HB wants to replace some part with some others as
\replaced[id=hb]{
	the new text
}{
	the old text
}

% =======================================
\subsection{Communicate with Footnotes}

Another way to communicate between authors is to use of footnotes
\hbFootnote{HB}{
	This is a footnote by HB.
}.
The other author has another footnote
\hbFootnote{AB}{
	This is a footnote by AB.
}
.
Note that this is not the same as regular footnotes that you intent to keep in your final document such as~\footnote{
	This is a footnote that should stay in the final version of the document.
}.
These communication footnotes should be removed at the end of development process.
Color of ``@HB'' at the start of the footnote should warn you, if you are looking the \hbDPdf\ file online.
One final search in the \hbDTex\ file for ``@'' should help you to locate unremoved ones.

% =======================================
\subsection{Lists}

This is an enumeration.
\begin{enumerate}

	\item 
	\textbf{Aaaa.}
	Describe Aaaa.

	\item 
	\textbf{Aaaa.}
	Describe Aaaa.

\end{enumerate}

% ========================================
\section{Math}

Please note the usage of spaces while writing math in \hbDTex\ file.
Proper usage of space will improve readability of your \LaTeX\ code.

This is math in line. 
The row sum of $i$ is given as
$
	a_{k \cdot} = \sum_{j=1}^{N} a_{i j}
$,
where $A = [a_{i j}]$ is a matrix.

If you want your math in display mode there are two options. 
If you are not going to refer it again, 
use \verb!\[ ... \]!, 
which produces
\[
	e_{\mu x} 
	= \frac{a_{\mu x}}{\sum_{x'=1}^{S} a_{\mu x'}},
	\quad
	d_{x \mu} 
	= \frac{a_{\mu x}}{\sum_{\mu'=1}^{M} a_{\mu'x}}.
\]
If you are going to refer it again, 
use \verb!\begin{align} ... \end{align}! to obtain
\begin{align}
	a_{ij} =
		\frac{1}{M}
		\sum_{\mu = 1}^{M} 
		{\sum_{x = 1}^{S} 
			e_{\mu x}^{(i)}
			d_{x \mu}^{(j)} }.
	\label{eq:aij}
\end{align}
If you have multiple line derivation,
then \hbCode{align} with \verb!&! is the solution.
\begin{align}
	a 
	&= bbbbb\\
	&= cccc\\
	&= ddd.
\end{align}
If you do not refer the equation later,
get rid off numbers by using 
\verb!\begin{align*} ... \end{align*}!
as
\begin{align*}
	a 
	&= bbbbb\\
	&= cccc\\
	&= ddd.
\end{align*}

% =======================================
\subsection{Referring to an Equation}

Refer an equation \refeq{eq:aij}.
You can refer to an equation \refeq{eq:kBar} in the appendix, too.

% =======================================
\subsection{Subscripts and superscripts}

Always use curly brackets when you use subscripts or superscripts 
even if there is no need due to single symbol.
For example \verb!a_{i}! is better than \verb!a_i! 
if you consider
\verb!a_{ij}! and \verb!a_ij!.
They produce
$a_{i}$,
$a_i$,
$a_{ij}$, and 
$a_ij$,
respectively.

% ========================================
\subsubsection{Comprehension}

Suppose agent $i$ wants to pass meaning $\mu$ to agent $j$.
Probability of doing this correctly is
\[
	\sum_{x = 1}^{S} 
		e_{\mu x}^{(i)}
		d_{x \mu}^{(j)} 
\]
where 
$e_{\mu x}^{(i)}$
and 
$d_{x \mu}^{(j)}$
are encoding of $i$ 
and decoding of $j$, 
respectively.
When we average that over all meanings,
we obtain \emph{comprehension} from $i$ to $j$, 
that is
If we want them to communicate both ways,
we consider \emph{mutual comprehension}
\[
	aaa{\hbSet{C}} = 	
	\frac{1}{2 {\hbAbs{\hbSet{C}} \choose 2}} 
	\sum_{i \in \hbSet{C}}
	\sum_{
		\substack{
			j \in \hbSet{C}\\
			j \neq i
		}
	} 
	{bb{i}{j}}.
\]

% ========================================
\subsection{$k$-means Clustering Algorithm}

% =======================================
\subsubsection{Finding Optimum Language Clusters}

\[
	Aaaa{K} =
		\argmax
			{K}
			{bbb{\mathbb{P}_{K}}}.
\]

% ========================================
\section{Figures}

Refer to a figure as \reffig{fig:FigWP.eps}.
If you want to refer to a figure with multiple graphs,
there is a way to refer all at once \reffig{fig:N100},
 or individually \reffig{fig:FigWStar} and \reffig{fig:FigKStar100} as required.

% +++++++++++++++++++++++++++++++++++++++
%: -fig.1
\begin{figure}[!tbp]
	\centering 
	\includegraphics[width=\columnwidth]%
		{FigIStar.eps}
	\caption{
		Single figure.
	} 
	% \caption
	\label{fig:FigWP.eps}
\end{figure}
% +++++++++++++++++++++++++++++++++++++++

% +++++++++++++++++++++++++++++++++++++++
%: -fig 2
\begin{figure}[!tbp]
	\begin{subfigure}{\columnwidth}%
		\includegraphics[width=\columnwidth]
			{FigWStar.eps}
		\caption{Within Community Comprehensions} 
		\label{fig:FigWStar}
	\end{subfigure}
	\begin{subfigure}{\columnwidth}%
		\includegraphics[width=\columnwidth]
			{FigIStar.eps}
		\caption{Inter-Community Comprehensions} 
		\label{fig:FigIStar}
	\end{subfigure}
	\begin{subfigure}{\columnwidth}%
		\includegraphics[width=\columnwidth]
			{FigKStar100.eps}
		\caption{Subcommunity Counts} 
		\label{fig:FigKStar100}
	\end{subfigure}
	\caption{
		Language subcommunities.
		$N = 100$.
	} % \caption
	\label{fig:N100}
\end{figure}
% +++++++++++++++++++++++++++++++++++++++

% ========================================
\section{References and citations}
\label{sec:ReferencesAndCitations}

Journals may have different ways to present references. 
If one use consistently the same macro for references,
simple change in the macro definition can solve 
the problem of adjusting from one journal to another.
There are a number of objects such as 
definitions \refdef{def:PositiveIntegerPowers}, 
examples \refexmp{exp:Generic},
figures, 
code listings \reflst{lst:QuickStart}
 that you can refer to.

% ========================================
\begin{defn}[Positive Integer Powers]
	For all $x \in \hSoX$, and $n \in \hSoN$
	\[
		x^{n} \triangleq
		\begin{cases}
			1, 
			 &n = 0, \\
			x, 
			 &n = 1, \\
			x x^{n-1},
			 &n > 1.
		\end{cases}
	\]
	\label{def:PositiveIntegerPowers}
\end{defn}

% ========================================
\begin{exmp}
	\label{exp:Generic}
	Note that $\hSoX$ is defined in a very generic way.
	We can take $\hSoX$ as 
	natural numbers $\hSoN$,
	real numbers $\hSoR$, or
	$N \times N$ real matrices $\hSoR_{N \times N}$.
\end{exmp}

% ========================================
\lstinputlisting[language=java,basicstyle=\tiny\ttfamily,label=lst:QuickStart,caption=Node object]
	{code-sample.java}

% ========================================
\subsection{References}

Any object that will be referred,
should have a label declaration such as
\verb!\label{A:B}!,
where 
$A$ is type indicator and
$B$ is unique label with in the type.
Commonly used type indicator are given in \reftbl{tbl:TypeIndicators}.
See ``HB Header Common Declarations'' in the source for more.

% +++++++++++++++++++++++++++++++++++++++
%: -table TypeIndicators
\begin{table}[th]
	\caption{Reference type indicators}
	\begin{center}
	\begin{tabular}{|l |l |l |l |}
		\hline
		Type
		&Indicator
		&Code
		&Result\\
		\hline
		%
		Equation
		&eq
		&\verb!\refeq!
		&\refeq{aaa}\\
		%
		Figure
		&fig
		&\verb!\reffig!
		&\reffig{aaa}\\
		%
		Table
		&tbl
		&\verb!\reftbl!
		&\reftbl{aa}\\
		%
		Section
		&sec
		&\verb!\refsec!
		&\refsec{aa}\\
		%
		Citation
		&-
		&\verb!\refcite!
		&\refcite{aa}\\
		%
		Definition
		&def
		&\verb!\refdef!
		&\refdef{aaa}\\
		%
		Theorem
		&thm
		&\verb!\refthm!
		&\refthm{aa}\\
		%
		Algorithm
		&alg
		&\verb!\refalg!
		&\refalg{aaa}\\
		%
		List
		&lst
		&\verb!\reflst!
		&\reflst{aa}\\
		%
		aaa
		&aaa
		&\verb!aaaa!
		&aaa\\
		\hline
	\end{tabular}
	\end{center}
	\label{tbl:TypeIndicators}
\end{table}%
% +++++++++++++++++++++++++++++++++++++++

It is possible to refer a number of objects within \LaTeX.
Refer an equation \refeq{eq:aij}, which can be obtained by \verb!\refeq{eq:aij}!. 
A figure can be referred by means of \verb!\reffig{fig:N100}!, which produces \reffig{fig:N100}.
Similarly a table can be referred by \reftbl{tbl:gamma} by using \verb!\reftbl{tbl:gamma}!.
A section can be referred by \refsec{sec:ReferencesAndCitations}, 
that is, 
\verb!\refsec{sec:ReferencesAndCitations}!.

% ========================================
\subsection{Citations}

Check the source to see how I prefer to cite~\cite{%
	duda2012pattern,
	mackay2003information,
	theodoridis2010patternMatlab}.
In this way, you can see the citations easily both in .tex and .pdf forms.
In .pdf file, citations are in color.
If you want to modify,
see 
\hbCode{linkcolor=red}
in 
\hbCode{hyperref}.
Use citation at  the end of sentence as much as possible.
Connect citation to the word with tilda as in the case here~\cite{%
	AAa2017bb}.
See the code.
If a sentence starts with citation,
start with \refcite{%
	AAa2017bb}  
not with \cite{%
	AAa2017bb}.

% =======================================
\subsection{Tables}

Refer to tables as \reftbl{tbl:gamma}.

% +++++++++++++++++++++++++++++++++++++++
%: -table 1
\begin{table}[th]
	\caption{$\gamma$ values for $r > 0.03$}
	\begin{center}
	\begin{tabular}{|r|cc|}
		\hline
		$N$
		&Model-A %\quad
		&Model-B\\
		\hline
		%
		50
		&0.72
		&0.62\\
		%
		100
		&0.69
		&0.63\\
		%
		150
		&0.72
		&0.69\\
		%
		200
		&0.68
		&0.72\\
		\hline
	\end{tabular}
	\end{center}
	\label{tbl:gamma}
\end{table}%
% +++++++++++++++++++++++++++++++++++++++

% =======================================
\appendix
%: ==== HB Header Common for Appendix v20170517 ====V
\newcommand{\hbAppendixPrefix}{A}
%
\renewcommand{\thefigure}{\hbAppendixPrefix\arabic{figure}}
\setcounter{figure}{0}
\renewcommand{\thetable}{\hbAppendixPrefix\arabic{table}} 
\setcounter{table}{0}
\renewcommand{\theequation}{\hbAppendixPrefix\arabic{equation}} 
\setcounter{equation}{0}
% ==== HB Header Common for Appendix v20170517 ====A

\section{Appendix}
\label{sec:appendix}

% =======================================
\subsection{$k$-means Algorithm}
	\label{sec:kMeansAlgorithm}

An equation
\begin{equation}
	\label{eq:kBar}
	\bar{k} = \argmin{k} d(\mathbf{x}_{n},  \mathbf{m}_{k}(t-1))
\end{equation}
is here.

% =======================================
\subsection{$k$-means in Language Domain}

%% =======================================
\section*{Acknowledgments}

%\textbf{Acknowledgments.}
This work was partially supported 
by Bogazici University Research Fund [BAP-2008-08A105], 
by the Turkish State Planning Organization (DPT) TAM Project [2007K120610], 
and 
by COST action TD1210.

% ========================================
\bibliographystyle{ieeetr}

\bibliography{Bingol-Template-Paper}

% =========
\listofchanges   % track changes use at the bottom
% =========

\end{document}

### 2019-03-01 bingol-LaTeX-Template-Paper/Bingol-Template-ResponseToReviewers.tex
no idea

% !TEX spellcheck = en_US

\documentclass[10.5pt]{amsart}
%: ==== HB Header Common Packages v20160423 ====V
	\usepackage[utf8]{inputenc} % To use Unicode characters
	\usepackage[iso]{datetime}
	\usepackage{amsmath, amssymb}
	%	\usepackage{etex}

	\usepackage[a4paper]{geometry}

	\usepackage{xcolor}
	% black, blue, brown, cyan, darkgray, gray, green, lightgray, lime, 
	% magenta, olive, orange, pink, purple, red, teal, violet, white, yellow
	\usepackage[colorlinks=true,linkcolor=red,urlcolor=blue,citecolor=red]%
		{hyperref}
	\usepackage{graphicx,epstopdf}
	% \graphicspath{{fig}}
	\graphicspath{{../common/figures/}}
	% \DeclareGraphicsExtensions{.pdf,.jpeg,.png,.eps}
	% \DeclareGraphicsRule{.tif}{png}{.png}%
	%	{`convert #1 `dirname #1`/`basename #1 .tif`.png}
%	\usepackage{subfigure}
\usepackage{subcaption}

%: ==== HB Header Common Declarations v20160423 ====V
	\newcommand{\hbTimeStamp}{{\color{red}--Draft-- v\today}} % version
	%
	\newcommand{\reffig}[1]{Fig.~\ref{#1}}
	\newcommand{\refeq}[1]{Eq.~\ref{#1}}
	\newcommand{\reftbl}[1]{Table~\ref{#1}}
	\newcommand{\refsec}[1]{Sec.~\ref{#1}}
	\newcommand{\refcite}[1]{Ref~\cite{#1}}
	\newcommand{\hbQuote}[1]{{\small \textsf{``#1''}}}
	%
	\newcommand{\refthm}[1]{Theorem~\ref{#1}}
	\newcommand{\refthmA}[2]{\refthm{#1}(\ref{#2}}
	\newcommand{\reflem}[1]{Lemma~\ref{#1}}
	\newcommand{\refdef}[1]{Definition~\ref{#1}}
	\newcommand{\refexmp}[1]{Example~\ref{#1}}
	%
	\newcommand{\hbFootnote}[2]{\footnote{{\color{red} @#1}#2}}
	\newcommand{\hbIdea}[1]{{\color{olive}{\scriptsize [{#1}]}}}
%	\newcommand{\hbIdea}[1]{} % Empty		
	%	\newcommand{\hbIdea}[1]{}
% ==== HB Header Common Declarations v20160423 ====A

%: ==== HB Header Common for Appendix v20170517 ====V
\renewcommand{\thefigure}{A\arabic{figure}}
\setcounter{figure}{0}
\renewcommand{\thetable}{A.\arabic{table}} 
\setcounter{table}{0}
% ==== HB Header Common for Appendix v20170517 ====A

%: ==== HB Header Common for RoR v20170517 ====V
% 	Response to Reviewer
%
\newcommand{\hbRoRCommonPoints}{``Common Points''}
%
\newcommand{\hbColorReviewer}{magenta}
\newcommand{\hbColorManuscript}{violet}
\newcommand{\hbColorManuscriptBackground}{yellow}
%
\usepackage{soul}
\sethlcolor{\hbColorManuscriptBackground}
%
\newenvironment{hbReviewer}
	{\list{}{\leftmargin=2cm\rightmargin=1cm}\item[]``\begin{footnotesize}
	\begin{color}{\hbColorReviewer}}	
	{\end{color}\end{footnotesize}''\endlist}

% connection to the manuscript
%\newcommand{\hbMRef}[1]{``\texttt{{\color{\hbColorManuscript}#1}}''}
\newcommand{\hbMRef}[1]{``\texttt{{\color{\hbColorManuscript}\hl{#1}}}''}
\newcommand{\hbMRefP}[2]{``\texttt{{\color{\hbColorManuscript}\hl{#1}}}''  (page~#2)}
%
%\newenvironment{hbChanged}
%	{\list{}{\leftmargin=0.5cm\rightmargin=1.5cm}\item[]``\begin{small}}	
%	{\end{small}''\endlist}
%
\newenvironment{hbChanged}
	{\list{}{\leftmargin=1cm\rightmargin=1.5cm}\item[]``\begin{small}
	\begin{color}{\hbColorManuscript}}	
	{\end{color}\end{small}''\endlist}
%
\newcommand{\hbMreffig}[1]{\hbMRef{Fig.~#1}}
\newcommand{\hbMreftbl}[1]{\hbMRef{Table.~#1}}

%  ==== HB Header Common for RoR v20170517 ====A

%: ======= reference to the main text ===============V
%% without pace no
%\newcommand{\hbMIntroduction}{\hbMRef{1. Introduction}}
%\newcommand{\hbMMotivation}{\hbMRef{1.1. Motivation}}
%\newcommand{\hbMBackground}{\hbMRef{2. Background}}
%\newcommand{\hbMLanguageModel}{\hbMRef{2.1. Language Model}}
%\newcommand{\hbMComprehension}{\hbMRef{2.1.1. Comprehension}}
%\newcommand{\hbMLearningModel}{\hbMRef{2.1.2. Learning Model}}
%\newcommand{\hbMKMeans}{\hbMRef{2.2. $k$-means Algorithm}}
%\newcommand{\hbMOptimumLanguageClusters}{\hbMRef{2.2.1. Finding Optimum Language Clusters}}
%\newcommand{\hbMModel}{\hbMRef{3. Model}}
%\newcommand{\hbMResultsAndDiscussion}{\hbMRef{4. Results and Discussion}}
%\newcommand{\hbMSubcommunities}{\hbMRef{4.1. Subcommunities}}
%\newcommand{\hbMNumberOfSubcommunities}{\hbMRef{4.2. Number of Subcommunities}}
%\newcommand{\hbMFutureWork}{\hbMRef{4.3. Future Work}}
%\newcommand{\hbMConclusion}{\hbMRef{5. Conclusions}}
%\newcommand{\hbMAppendix}{\hbMRef{Appendix A}}
%\newcommand{\hbMKMeansAlgorithm}{\hbMRef{A.1. $k$-means Algorithm}}
%\newcommand{\hbMKMeansLanguageDomain}{\hbMRef{A.2. $k$-means in Language Domain}}
% with page no
\newcommand{\hbMIntroduction}{\hbMRefP{1. Introduction}{1}}
\newcommand{\hbMMotivation}{\hbMRefP{1.1. Motivation}{1}}
\newcommand{\hbMBackground}{\hbMRefP{2. Background}{2}}
\newcommand{\hbMLanguageModel}{\hbMRefP{2.1. Language Model}{2}}
\newcommand{\hbMComprehension}{\hbMRefP{2.1.1. Comprehension}{2}}
\newcommand{\hbMLearningModel}{\hbMRefP{2.1.2. Learning Model}{3}}
\newcommand{\hbMKMeans}{\hbMRefP{2.2. $k$-means Algorithm}{3}}
\newcommand{\hbMOptimumLanguageClusters}{\hbMRefP{2.2.1. Finding Optimum Language Clusters}{3}}
\newcommand{\hbMModel}{\hbMRefP{3. Model}{4}}
\newcommand{\hbMResultsAndDiscussion}{\hbMRefP{4. Results and Discussion}{5}}
\newcommand{\hbMSubcommunities}{\hbMRefP{4.1. Subcommunities}{5}}
\newcommand{\hbMNumberOfSubcommunities}{\hbMRefP{4.2. Number of Subcommunities}{6}}
\newcommand{\hbMFutureWork}{\hbMRefP{4.3. Future Work}{7}}
\newcommand{\hbMConclusion}{\hbMRefP{5. Conclusions}{7}}
\newcommand{\hbMAppendix}{\hbMRefP{Appendix A}{8}}
\newcommand{\hbMKMeansAlgorithm}{\hbMRefP{A.1. $k$-means Algorithm}{8}}
\newcommand{\hbMKMeansLanguageDomain}{\hbMRefP{A.2. $k$-means in Language Domain}{8}}
%  ======= reference to the main text ===============V

%: ======= specific ===============
\DeclareGraphicsExtensions{.png}
%
\newcommand{\hbAbs}[1]{| #1 |}
\newcommand{\hbNorm}[1]{\left\lVert #1 \right\rVert}
%
\DeclareMathOperator{\sgn}{sgn}
\DeclareMathOperator{\cov}{cov}
\newcommand{\argmin}[2]{\underset{#1}{\operatorname{arg \, min}}\;#2}
\newcommand{\argmax}[2]{\underset{#1}{\operatorname{arg \, max}}\;#2}
%\newcommand{\hbAvg}[1]{\widehat{#1}}
\newcommand{\hbOpt}[1]{{#1}^*}
\newcommand{\hbMat}[1]{\mathbf{#1}}
\newcommand{\hbSet}[1]{\mathcal{#1}}
%\newcommand{\hbPartition}{[1]}{\mathbb{#1}}
%\newcommand{\hbIndSet}[2]{\mathcal{#1}_{#2}}
%\newcommand{\hbLS}[2]{F( #1 , #2 )}
\newcommand{\hbLS}[2]{F( #1 \leftrightarrow #2 )}
\newcommand{\hbDLS}[2]{F( #1 \to #2 )}
\newcommand{\hbPayoff}[1]{F_{#1}}
\newcommand{\hbInCLS}[1]{W(#1)}
\newcommand{\hbInCLSrandom}[1]{W_{\text{r}}(#1)}
\newcommand{\hbOptInCLS}[1]{\hbOpt{W}(#1)}
\newcommand{\hbDIntCLS}[2]{I({#1 \to #2})}
%\newcommand{\hbIntCLS}[2]{I(#1, #2)}
\newcommand{\hbIntCLS}[2]{I(#1 \leftrightarrow #2)}
\newcommand{\hbPartition}[1]{\mathbb{#1}} % partition P
\newcommand{\hbPartitionBest}[1]{\overline{\hbPartition{P}_{#1}}} % best partition Pwith K-blocks
%\newcommand{\hbPartitionBest}[1]{\hbPartition{P}_{#1}^{*}} % best partition Pwith K-blocks
\newcommand{\hbMBase}{Base Model}
\newcommand{\hbMA}{Model-A}
\newcommand{\hbMB}{Model-B}
\newcommand{\hbMAB}{Models~A and B}
\newcommand{\hbMC}{Model-C}

\newcommand{\hbIC}[2]{I( #1 \leftrightarrow #2 )}

% ======= specific ===============

\begin{document}
\title[Parent Oriented Teacher Selection Causes Language Diversity]{
	Response to Reviewers\\
	~\\
	~\\
	{\footnotesize
		``Parent Oriented Teacher Selection Causes Language Diversity''\\
		version Dated Feb 20, 2017
	}
}
\author{Ibrahim Cimentepe}
\author{Haluk O. Bingol}
%\affiliation{
%	Department of Computer Engineering\\
%	Bogazici University, Istanbul \\
%	%\today 
%}

\date{\today}
%\date{\hbTimeStamp}

\maketitle

% ======================
\section{Introduction}

We would like to thank our anonymous reviewers 
for pointing out corrections, suggesting ideas and references.
They were very useful and help us to improve readability of the manuscript.

% =======================================
\subsection{Organization}

This response to reviewer is organized as follows.
Individual points are listed under the corresponding reviewers.
Common points that are raised by multiple reviewers 
are addressed in  \refsec{sec:CommonPoints} \hbRoRCommonPoints.

% =======================================
\subsection{Markup in the manuscript}

Changes in the manuscript are highlighted and marked with section number of points.
For example,
changes related to the point
``How $k$-means adapted to language'', 
which is in section 2.2.1,
is marked with 2.2.1.

% =======================================
\subsection{Conventions}

\newcommand{\hbMSample}{\hbMRef{Introduction}}

In order to distinguish 
%
(i)~comments of the reviewers, 
%
(ii)~responses given to the comments, 
%
(iii)~references to the manuscript, and 
%
(iv)~changes done in the manuscript, 
some format, font and color combinations are used.

\begin{hbReviewer}
	This is a sample of comments of reviewer.
	Quotes of the comments of reviewer are given in this format.
\end{hbReviewer}

This is a sample response to the points raised by the reviewer.
During the response, 
one needs to refer to a figure in the manuscript by 
\hbMreffig{3a}.
A section title in the manuscript can be given as \hbMSample.

\begin{hbChanged}
	This is a sample of changes done.
	If one needs to quote the changes done in the manuscript,
	they are given in this format.
\end{hbChanged}

% ======================
\section{Report to the Reviewer \#1}

% =======================================
\subsection{General}
\begin{hbReviewer}
	The authors consider an existing model that describes how language could
	evolve when transferred from one generation to another and extended it
	to the setting in which each offspring learns their language from a particular
	individual who is either geographically or language-wise close to the parent
	of that offspring. They find that such an extended model can promote
	emergence of several subcommunities that share a language, as opposed to
	a global community sharing a universal language.

	I like the idea of the work. Such an extension seems natural and the findings
	are interesting. The paper is well structured and once the reader gets used to
	omnipresent typos it reads quite smoothly. I have three major comments
	and several minor suggestions that I list below (page X,line Y):
\end{hbReviewer}

Thanks.

% =======================================
\subsection{Major Points}

% =======================================
\subsubsection{How $k$-means adapted to language}
\begin{hbReviewer}
	p3,l74:
	I very much like the idea of using the k-means clustering algorithm but
	I'd like to see in more detail how it is adapted to the language domain 
	(possibly in an Appendix).
	For example, as far as I know, in the traditional k-means algorithm,
	at some point one takes the ``centers'' of each current cluster.
	I don't see how this is done in the adaptation 
	which renders the findings of the paper irreproducible. 
\end{hbReviewer}

We agree that our $k$-means adaptation to language domain 
is not given properly.
As suggested, an \hbMAppendix\ is added. 
First $k$-means description in $\mathbb{R}^{D}$ is given.
Then adaptation of $k$-means to language domain is described. 
How to handle ``centers''  in the domain of language is disguised in detail.

% =======================================
\subsubsection{Clusters vs language communities}
\label{sec:ClustersLanguageCommunities}
\begin{hbReviewer}
	p4,l11:
	While I agree that defining average within community comprehension and
	taking K that maximizes it is the most natural thing to do, I'd like to see some
	discussion of why such clusters should correspond to language communities 
	 (as in p7,l25).
	For example, in principle it might happen that 
	 the people with worst mutual understanding
	are all lumped together into one cluster, even though, logically, 
	 they are not a single
	language community.
	(This might be checkable by looking at minimum 
	 within community comprehension.)
\end{hbReviewer}

Thanks for pointing this important issue.
%By definition, $k$-means algorithm is forced to organize $K$ clusters.
%If the nature of the data set is not agree with the selected value of $K$,
%the clusters would not make sense.
%%It is very possible that $k$-means points clusters 
%%that are not well suited to language communities.
%That is, 
%it may group agents that do not ``speak'' the same language in a cluster.
%
%This issue is addressed in different sections.
%
The concept of inter-community comprehension is introduced in
section \hbMOptimumLanguageClusters\ and 
\hbMreffig{2b} is given and  discussed in \hbMSubcommunities.\\
Please see \refsec{sec:diversity} for details.

Potential problems of $k$-means algorithm are discussed in the \hbMAppendix.

%One potential source of problem, 
%that comes with $k$-means algorithm,
%is the selection of $K$ not suitable to the data set.
%Our adaptation carries the same weaknesses.
%This is addressed in different sections.
%(i)~Section \hbMOptimumLanguageClusters\ discusses 
%finding the ``best'' $K$ for the data set and 
%why clusters are expected to be language communities.
%%
%(ii)~In the section on \hbMFutureWork, 
%some discussion on this problem is added, too.
%%
%(iii)~Potential problems of $k$-means algorithm are discussed in the \hbMAppendix.

% =======================================
\subsubsection{``Kˆ* is independent of .. N''}
\begin{hbReviewer}
	p6,l58:
	I don't quite agree with the (bold) statement  "K\^{}* is independent of .. N".
	In Figure 3, the red data points (N=50) seem to be mostly above the green ones (N=100),
	which seem to be in turn mostly above the blue and purple ones (N=150,200).
	To me, that seems like a dependence on N, although a weak one.
	I'd suggest putting the statement more mildly.
\end{hbReviewer}

%\newcommand{\hbMAB}{Models~A and B}
%\newcommand{\hbOpt}[1]{{#1}^*}

We agree that the statement
``We conclude that for \hbMAB,
the optimum community count $\hbOpt{K}$ is 
independent of the size of the population $N$'' 
is difficult to justify. 
The discussion of \hbMreffig{3} in \hbMNumberOfSubcommunities\ is revised  accordingly.
Now it reads:
\begin{hbChanged}
	(ii)~There is a weak relation between $K^{*}$ and $N$.
	For each model, 
	the value of $K^{*}$ is slightly less for larger values of $N$.
\end{hbChanged}

% =======================================
\subsubsection{Gamma values}
	\label{sec:AGammaValues}
\begin{hbReviewer}
	On a related note, what is gamma, empirically, for N=50, 100, 150, 200?
\end{hbReviewer}

For $\gamma$ values, please see \refsec{sec:R2PowerLaw} in \hbRoRCommonPoints.

% =======================================
\subsection{Minor Points}

% =======================================
\subsubsection{p3,l12:}
\begin{hbReviewer}
	p3,l12:
	I suggest "Language evolves \_both\_ through .. \_and\_ as .."
\end{hbReviewer}

Thanks for the correction. It is done.
Now, in \hbMLearningModel, it reads:
\begin{hbChanged}
	Language evolves
	both through agents interacting with each other within a  generation, 
	and as it is transferred from one generation to the next by means of learning.
\end{hbChanged}

% =======================================
\subsubsection{p4,l5:}
\begin{hbReviewer}
	p4,l5:
	This sentence might be misleading. 
	I believe the selected partition is not necessarily the optimal one but 
	the one found by the algorithm 
	(which is, I agree, probably reasonably close to the optimal one). 
	I suggest putting the sentence more mildly.
\end{hbReviewer}

It is true that $k$-means may not provide the optimum partition but near optimum is expected. 
The wording in \hbMOptimumLanguageClusters\
is changed accordingly.
Now it reads:
\begin{hbChanged}
	For a given $K$,
	$k$-means algorithm provides partition
	$\hbPartitionBest{K}$,
	which is expected to be close to the partition with
	the maximum 
	average within community comprehension.
\end{hbChanged}

% =======================================
\subsubsection{p5,l4:}
\begin{hbReviewer}
	p5,l4:
	Parameters M, S, Q are set to some specific values. 
	Is there anything to be said about the dependence on them?
\end{hbReviewer}

In principle parameters $M$, $S$, $Q$ are independent and
can be selected in any way.
For example, Ref~\cite{nowak1999JTB} uses $M = S = 5$ and $Q = 1, 4, 7, 10$.
%Ref~\cite{nowak2000evolution} uses $M = S = 4$ and $M = S = $
Ref~\cite{nowak1999PNAS} uses $M = 20 < S = 40$.

We prefer to report the case, 
where there are more symbols than meanings.
i.e. $M < S$ .
We used the values $M = 8 < S = 15$ and $Q = 4$.
We also investigate $(5,5), (5,8), (8,5)$ and $(8,8)$ values for $(M, S)$.
Different sampling sizes $Q = 1, 4, 7, 10$ are tested.
We found that the quality of language is low for Q = 1, 
whereas it gets higher and 
stays approximately the same for Q = 4, 7 and 10. 
Therefore Q = 4 seems to be the reasonable selection in our simulation.
As previously reported, 
$Q = 1$ slows down learning since it is too little sampling to learn from teacher.

Since there is not much to say, no change is made in the manuscript.

% =======================================
\subsubsection{p5,l5:}
\begin{hbReviewer}
	p5,l5:
	What are the association matrices of the first generation?
\end{hbReviewer}

You are right that this points is missing. 
\hbMModel\ section is changed accordingly.
Now it reads:
\begin{hbChanged}
	The system starts with the first generation,
	whose  association matrices are randomly filled.
	Remaining generations fill their association matrices by learning.
	Every agent $i$ makes exactly one child $i'$.
	The association matrix of a child is initially empty.
	Each child learns her language from her \emph{teacher},
	donated by $t_{i}$.
\end{hbChanged}

% =======================================
\subsubsection{p6,l51:}
\begin{hbReviewer}
	p6,l51: 
	The word "implies" sounds too strong to me, I'd consider "suggests" or 
	the elsewhere frequent "indicates".
\end{hbReviewer}

Thanks for the correction.
``Implies'' is replaced by ``suggests'' in \hbMNumberOfSubcommunities.
Now it reads:
	\begin{hbChanged}
	The shape of the curve in 
	Fig.~2c %\reffig{fig:FigKStar100}
	suggests a power law relation between $\hbOpt{K}$ and $r$, 
	that is,
\end{hbChanged}

% =======================================
\subsubsection{Highlights:}
\begin{hbReviewer}
	I suggest 
	"ones talk" $->$ "someone who talks", 
	"ones that are" $->$ "someone who is", 
	"effects" $->$ "affects"
\end{hbReviewer}

Thanks for the corrections. They are done.

%% ======================
%\newpage

% ======================
\section{Report to the Reviewer \#2}

%================================================
\subsection{General}
\begin{hbReviewer}
	This work extends a previous mathematical model 
	to study language learning from parents to offspring, 
	and studies two types of strategies to select teachers to communicate. 
	It is shown that the two types of strategies induce language diversity 
	after iterated learning across generations of learners. 
	It also finds a power-law relation between the optimal comprehension level 
	and the size of imitation set for selecting teachers. 
	The mathematical parts of the model are solid, 
	and the results are convincing (though see below). 
	It is a topic suitable for JTB. 
	However, there are several concerns 
	that need to be addressed before this simple work can be published. 
\end{hbReviewer}

Thanks.

% =======================================
\subsection{Gong \& Shuai 2012 Proceeding B}
\begin{hbReviewer}
	First, in the background part, 
	the authors only reviewed previous mathematical models 
	from Nowak's group 
	and briefly mentioned some behavioral models of iterated learning 
	and similar laboratory experiments. 
	However, the idea of learning to people 
	that have high comprehension score during cross-generational learning 
	has been implemented in some behavioral models, 
	such as Gong \& Shuai 2012 Proceeding B. 
	In that work, cultural transmission (selection) is based on 
	individuals' linguistic understandability. 
	This work should be mentioned, 
	since the idea of the current paper is not new. 
\end{hbReviewer}

Thank for pointing out this missing reference.
\hbMIntroduction\ is revised accordingly.
Now it reads:
\begin{hbChanged}
	Yet another group consider language 
	as a means to transfer meanings between individuals
	through signaling structures~[8-10].
	%~\cite{%
	%	nowak2002computational,
	%	gong2012coevolution,
	%	kirby2007innateness}.''
\end{hbChanged}
where Ref~[9] is Gong and Shuai 2012.

% =======================================
\subsection{Comprehension scores of both models are already above 0.125}
\begin{hbReviewer}
	Second, in the result part, there are some confusing points. 
	For example, on page 5, above "Subcommunities", the authors said: 
	"In Fig. 1, comprehensions of both Models A and B are
	 below the threshold of $W_{r}(\mathcal{P}) = 0.125$ for $r < 0.05$". 
	However, it is quite clear in that Fig. 1, 
	except under a small $r < 0.05$, 
	comprehension scores of both models are already above 0.125. 
	Please specify this.
\end{hbReviewer}

We agree that wording was not good.
It is changed accordingly in \hbMResultsAndDiscussion.
Now it reads:
\begin{hbChanged}
	In 
	Fig.~1, %\reffig{fig:FigWP.eps},
	comprehensions of both \hbMAB\ are below 
	the threshold of $\hbInCLSrandom{\hbSet{P}} = 0.125$ 
	for $r < 0.05$.
	The comprehensions increase slowly and reach to the level of \hbMC\ 
	as $r$ approaches to $0.5$.
\end{hbChanged}

% =======================================
\subsection{Diversity}
\label{sec:diversity}
\begin{hbReviewer}
	In addition, since the authors talk about "diversity", 
	only showing within community comprehension score is insufficient, 
	you need to also show comprehension score between communities, 
	in this way, people can really have a sense that the system is diverge! 
	Showing the average comprehension score of all communities is also 
	not enough, 
	because it is possible that the low average score is simply 
	due to low score of some community, 
	and between communities, comprehension score is still high; 
	in other words, every community is trying to develop the common language, 
	but some communities are delayed, 
	so the average score of all communities is not high. 
	This is certainly not divergent! 
\end{hbReviewer}

%This was the most challenging point.
We agree that our presentation was focused on within community comprehension.
We have revised the material and 
included discussion of inter-community comprehension, too.
Inter-community comprehension 
$\hbIntCLS{\hbSet{C}_{\alpha}}{\hbSet{C}_{\beta}}$ 
and 
average inter-community comprehension 
$I({\hbPartition{P}_{K}})$
are defined in \hbMOptimumLanguageClusters.
As suggested, 
average inter-community comprehension are given in \hbMreffig{2b} and discussed in \hbMSubcommunities.

Please also see \refsec{sec:ClustersLanguageCommunities}.

% =======================================
\subsection{Single teacher}
\label{sec:singleTeacher}
\begin{hbReviewer}
	Furthermore, the setting that each child only learns from a single parent 
	throughout the learning process is not realistic at all. 
	Teachers should be chosen proportionally 
	and there must be more than one learning cycle. 
	This actually introduces some noise, 
	because in this process, some individual from the imitation set 
	having low comprehension score can still be chosen, 
	which may delay or even reverse the divergence process. 
	Since most parts of the model are already based on probabilities, 
	the learning part should also be like this, 
	simply by setting more than one learning cycle for each child 
	and let teachers in those cycles be chosen probabilistically. 
\end{hbReviewer}

We agree that having single teacher is too much abstraction but an effective one.
Effects of having many teachers can be investigated as 
it is stated in the \hbMFutureWork\ section.
But we feel that it is not in the scope of this paper.
Now it reads:
\begin{hbChanged}
	For example,
	evolution of language can be perceived as a cultural process
	where some group of people is responsible for the transfer.
	That is, more than one teacher could be assigned to each child.
\end{hbChanged}

% =======================================
\subsection{Power law}
	\label{sec:BPowerLaw}

\begin{hbReviewer}
	Finally, in order to show that the relation between K and r is power-law, 
	why not draw Fig. 3 in a log-log scale to see 
	if there are straight lines or not. In addition, 
	some more discussion on this point is needed. 
\end{hbReviewer}

Please see \refsec{sec:R2PowerLaw} in \hbRoRCommonPoints.

% =======================================
\subsection{Cross-generational cultural transmission}
\begin{hbReviewer}
	Third, in the future work, 
	it would be interesting to further study 
	if grandparent grandchild interactions can help keep language 
	from divergence. 
	This can be simply implemented by keeping the grandparent's status 
	and let child have a chance to learning from them, 
	following exactly the same setting for him/her to learn 
	from parent generation. 
	Some early work like 
	Gong \& Shuai 2015 book chapter: 
	Simulating the effects of cross-generational cultural transmission 
	on language change 
	has addressed this based on a behavioral model. 
	A mathematical model like the one in the current paper 
	may complement the findings. 
\end{hbReviewer}

We agree that,
although it is interesting,
we do not consider the impact of grandparents and their generation in this work.
Probably one should consider this together with 
multi-teacher case of \refsec{sec:singleTeacher} as a future study.
We update the \hbMFutureWork\ section. 
It states the possibility of teachers from the generation of grandparents.
Now it reads:
\begin{hbChanged}
	Once many teachers case is considered,
	one may also consider teachers not only from the parent's generation but 
	the generation of grandparents, too~[20].
%	~\cite{%
%		gong2016CrossGenerational}.
\end{hbChanged}
where Ref~[20] is Gong and Shuai 2015.

% =======================================
\subsection{Some tiny points:}
\begin{hbReviewer}
Some tiny points:

1) page 7, right column, line 6: "effect" should be "affect"

2) page 7, right column, line 14: "which we communicate" should be "whom we communicate"
\end{hbReviewer}

Thanks for the corrections. They are done.

% ======================
\section{Common Points}
	\label{sec:CommonPoints}

Common points that are raised by both reviewers are addressed here.

% =======================================
\subsection{Power law discussion}
\label{sec:R2PowerLaw}

Issues related to power law are raised in 
\refsec{sec:AGammaValues} 
and 
\refsec{sec:BPowerLaw}.

Section \hbMNumberOfSubcommunities\ in the manuscript is modified to enhance power law discussion. 
Now \hbMreffig{3}\ has the same values in both linear-linear and log-log scale.
Discussion of straight-line patterns in log-log plot is included 
in \hbMNumberOfSubcommunities.
$\gamma$ values of Model-A and Model-B for various $N$ 
can be seen in \reffig{fig:Gamma}.
These values are given as \hbMreftbl{1} in the manuscript.

% +++++++++++++++++++++++++++++++++++++++
%:-fig gamma
\begin{figure}[!thbp]
	\centering 
	\includegraphics[width=\columnwidth]%
		{FigGamma.eps}
	\caption{
		$\gamma$ values of Model-A and Model-B for various $N$.
	} % \caption
	\label{fig:Gamma}
\end{figure}
% +++++++++++++++++++++++++++++++++++++++

% ========================================
\bibliographystyle{ieeetr}
\bibliography{EoLv5}

\end{document}

### 2019-03-01 bingol-LaTeX-Template-Paper/Bingol-Template-Paper.tex
no idea

@@
 \affiliation{
-	Deptment of Computer Engineering,\\
+	Department of Computer Engineering,\\
 	Bogazici University\\
@@
 		&\verb!\refeq!
-		&\refeq{aaa}\\
+		&\refeq{eq:kBar}\\
 		%
@@
 		&\verb!\reffig!
-		&\reffig{aaa}\\
+		&\reffig{fig:FigIStar}\\
 		%
@@
 		&\verb!\reftbl!
-		&\reftbl{aa}\\
+		&\reftbl{tbl:gamma}\\
 		%
@@
 		&\verb!\refsec!
-		&\refsec{aa}\\
+		&\refsec{sec:kMeansAlgorithm}\\
 		%
@@
 		&\verb!\refcite!
-		&\refcite{aa}\\
+		&\refcite{duda2012pattern}\\
 		%
@@
 		&\verb!\refdef!
-		&\refdef{aaa}\\
+		&\refdef{def:PositiveIntegerPowers}\\
 		%
@@
 		&\verb!\reflst!
-		&\reflst{aa}\\
+		&\reflst{lst:QuickStart}\\
 		%
@@
 If a sentence starts with citation,
-start with \refcite{%
+start with~\refcite{%
 	AAa2017bb}  
-not with \cite{%
+not with~\cite{%
 	AAa2017bb}.

### 2020-05-06 bingol-Tools/tex2eps.sh
tex2eps bash and homework template.

@@ -1,0 +1,11 @@
+#! /bin/bash
+
+# source: https://tex.stackexchange.com/questions/244831/convert-tikz-to-eps-using-pdflatex
+
+# converts a LaTeX to eps
+
+
+OUTPUT="_output"
+
+latex --jobname=${OUTPUT} ${1}
+dvips -o ${OUTPUT}.eps ${OUTPUT}.dvi

### 2021-03-05 bingol-StudentDirectory/0readme/bingol-template-paper/code-sample.java
reorganisation under student directory

@@ -1,0 +1,11 @@
+public class Node {
+	String name;
+	String lastName;
+	Node link;
+
+	public Node(){
+		name ="";
+		lastName="";
+		link = null;
+	}
+}

### 2021-03-05 bingol-template-paper/bingol-template-R2R.tex
More reorganisations.

% !TEX spellcheck = en_US

% ======================================= V
% (NC) 2019 Haluk Bingol
% github.com/halukbingol/LaTeX-Templates
%
% Licensees may copy, distribute, display, and perform the work and make derivative works 
% and remixes based on it only for non-commercial purposes. 
% ======================================= A

\documentclass[10.5pt]{amsart}
%: ==== HB Header Common Packages v20160423 ====V
	\usepackage[utf8]{inputenc} % To use Unicode characters
	\usepackage[iso]{datetime}
	\usepackage{amsmath, amssymb}
	%	\usepackage{etex}

	\usepackage[a4paper]{geometry}

	\usepackage{xcolor}
	% black, blue, brown, cyan, darkgray, gray, green, lightgray, lime, 
	% magenta, olive, orange, pink, purple, red, teal, violet, white, yellow
	\usepackage[colorlinks=true,linkcolor=red,urlcolor=blue,citecolor=red]%
		{hyperref}
	\usepackage{graphicx,epstopdf}
	% \graphicspath{{fig}}
	\graphicspath{{../common/figures/}}
	% \DeclareGraphicsExtensions{.pdf,.jpeg,.png,.eps}
	% \DeclareGraphicsRule{.tif}{png}{.png}%
	%	{`convert #1 `dirname #1`/`basename #1 .tif`.png}
%	\usepackage{subfigure}
\usepackage{subcaption}

%: ==== HB Header Common Declarations v20160423 ====V
	\newcommand{\hbTimeStamp}{{\color{red}--Draft-- v\today}} % version
	%
	\newcommand{\reffig}[1]{Fig.~\ref{#1}}
	\newcommand{\refeq}[1]{Eq.~\ref{#1}}
	\newcommand{\reftbl}[1]{Table~\ref{#1}}
	\newcommand{\refsec}[1]{Sec.~\ref{#1}}
	\newcommand{\refcite}[1]{Ref~\cite{#1}}
	\newcommand{\hbQuote}[1]{{\small \textsf{``#1''}}}
	%
	\newcommand{\refthm}[1]{Theorem~\ref{#1}}
	\newcommand{\refthmA}[2]{\refthm{#1}(\ref{#2}}
	\newcommand{\reflem}[1]{Lemma~\ref{#1}}
	\newcommand{\refdef}[1]{Definition~\ref{#1}}
	\newcommand{\refexmp}[1]{Example~\ref{#1}}
	%
	\newcommand{\hbFootnote}[2]{\footnote{{\color{red} @#1}#2}}
	\newcommand{\hbIdea}[1]{{\color{olive}{\scriptsize [{#1}]}}}
%	\newcommand{\hbIdea}[1]{} % Empty		
	%	\newcommand{\hbIdea}[1]{}
% ==== HB Header Common Declarations v20160423 ====A

%: ==== HB Header Common for Appendix v20170517 ====V
\renewcommand{\thefigure}{A\arabic{figure}}
\setcounter{figure}{0}
\renewcommand{\thetable}{A.\arabic{table}} 
\setcounter{table}{0}
% ==== HB Header Common for Appendix v20170517 ====A

%: ==== HB Header Common for RoR v20170517 ====V
% 	Response to Reviewer
%
\newcommand{\hbRoRCommonPoints}{``Common Points''}
%
\newcommand{\hbColorReviewer}{magenta}
\newcommand{\hbColorManuscript}{violet}
\newcommand{\hbColorManuscriptBackground}{yellow}
%
\usepackage{soul}
\sethlcolor{\hbColorManuscriptBackground}
%
\newenvironment{hbReviewer}
	{\list{}{\leftmargin=2cm\rightmargin=1cm}\item[]``\begin{footnotesize}
	\begin{color}{\hbColorReviewer}}	
	{\end{color}\end{footnotesize}''\endlist}

% connection to the manuscript
%\newcommand{\hbMRef}[1]{``\texttt{{\color{\hbColorManuscript}#1}}''}
\newcommand{\hbMRef}[1]{``\texttt{{\color{\hbColorManuscript}\hl{#1}}}''}
\newcommand{\hbMRefP}[2]{``\texttt{{\color{\hbColorManuscript}\hl{#1}}}''  (page~#2)}
%
%\newenvironment{hbChanged}
%	{\list{}{\leftmargin=0.5cm\rightmargin=1.5cm}\item[]``\begin{small}}	
%	{\end{small}''\endlist}
%
\newenvironment{hbChanged}
	{\list{}{\leftmargin=1cm\rightmargin=1.5cm}\item[]``\begin{small}
	\begin{color}{\hbColorManuscript}}	
	{\end{color}\end{small}''\endlist}
%
\newcommand{\hbMreffig}[1]{\hbMRef{Fig.~#1}}
\newcommand{\hbMreftbl}[1]{\hbMRef{Table.~#1}}

%  ==== HB Header Common for RoR v20170517 ====A

%: ======= reference to the main text ===============V
%% without pace no
%\newcommand{\hbMIntroduction}{\hbMRef{1. Introduction}}
%\newcommand{\hbMMotivation}{\hbMRef{1.1. Motivation}}
%\newcommand{\hbMBackground}{\hbMRef{2. Background}}
%\newcommand{\hbMLanguageModel}{\hbMRef{2.1. Language Model}}
%\newcommand{\hbMComprehension}{\hbMRef{2.1.1. Comprehension}}
%\newcommand{\hbMLearningModel}{\hbMRef{2.1.2. Learning Model}}
%\newcommand{\hbMKMeans}{\hbMRef{2.2. $k$-means Algorithm}}
%\newcommand{\hbMOptimumLanguageClusters}{\hbMRef{2.2.1. Finding Optimum Language Clusters}}
%\newcommand{\hbMModel}{\hbMRef{3. Model}}
%\newcommand{\hbMResultsAndDiscussion}{\hbMRef{4. Results and Discussion}}
%\newcommand{\hbMSubcommunities}{\hbMRef{4.1. Subcommunities}}
%\newcommand{\hbMNumberOfSubcommunities}{\hbMRef{4.2. Number of Subcommunities}}
%\newcommand{\hbMFutureWork}{\hbMRef{4.3. Future Work}}
%\newcommand{\hbMConclusion}{\hbMRef{5. Conclusions}}
%\newcommand{\hbMAppendix}{\hbMRef{Appendix A}}
%\newcommand{\hbMKMeansAlgorithm}{\hbMRef{A.1. $k$-means Algorithm}}
%\newcommand{\hbMKMeansLanguageDomain}{\hbMRef{A.2. $k$-means in Language Domain}}
% with page no
\newcommand{\hbMIntroduction}{\hbMRefP{1. Introduction}{1}}
\newcommand{\hbMMotivation}{\hbMRefP{1.1. Motivation}{1}}
\newcommand{\hbMBackground}{\hbMRefP{2. Background}{2}}
\newcommand{\hbMLanguageModel}{\hbMRefP{2.1. Language Model}{2}}
\newcommand{\hbMComprehension}{\hbMRefP{2.1.1. Comprehension}{2}}
\newcommand{\hbMLearningModel}{\hbMRefP{2.1.2. Learning Model}{3}}
\newcommand{\hbMKMeans}{\hbMRefP{2.2. $k$-means Algorithm}{3}}
\newcommand{\hbMOptimumLanguageClusters}{\hbMRefP{2.2.1. Finding Optimum Language Clusters}{3}}
\newcommand{\hbMModel}{\hbMRefP{3. Model}{4}}
\newcommand{\hbMResultsAndDiscussion}{\hbMRefP{4. Results and Discussion}{5}}
\newcommand{\hbMSubcommunities}{\hbMRefP{4.1. Subcommunities}{5}}
\newcommand{\hbMNumberOfSubcommunities}{\hbMRefP{4.2. Number of Subcommunities}{6}}
\newcommand{\hbMFutureWork}{\hbMRefP{4.3. Future Work}{7}}
\newcommand{\hbMConclusion}{\hbMRefP{5. Conclusions}{7}}
\newcommand{\hbMAppendix}{\hbMRefP{Appendix A}{8}}
\newcommand{\hbMKMeansAlgorithm}{\hbMRefP{A.1. $k$-means Algorithm}{8}}
\newcommand{\hbMKMeansLanguageDomain}{\hbMRefP{A.2. $k$-means in Language Domain}{8}}
%  ======= reference to the main text ===============V

%: ======= specific ===============
\DeclareGraphicsExtensions{.png}
%
\newcommand{\hbAbs}[1]{| #1 |}
\newcommand{\hbNorm}[1]{\left\lVert #1 \right\rVert}
%
\DeclareMathOperator{\sgn}{sgn}
\DeclareMathOperator{\cov}{cov}
\newcommand{\argmin}[2]{\underset{#1}{\operatorname{arg \, min}}\;#2}
\newcommand{\argmax}[2]{\underset{#1}{\operatorname{arg \, max}}\;#2}
%\newcommand{\hbAvg}[1]{\widehat{#1}}
\newcommand{\hbOpt}[1]{{#1}^*}
\newcommand{\hbMat}[1]{\mathbf{#1}}
\newcommand{\hbSet}[1]{\mathcal{#1}}
%\newcommand{\hbPartition}{[1]}{\mathbb{#1}}
%\newcommand{\hbIndSet}[2]{\mathcal{#1}_{#2}}
%\newcommand{\hbLS}[2]{F( #1 , #2 )}
\newcommand{\hbLS}[2]{F( #1 \leftrightarrow #2 )}
\newcommand{\hbDLS}[2]{F( #1 \to #2 )}
\newcommand{\hbPayoff}[1]{F_{#1}}
\newcommand{\hbInCLS}[1]{W(#1)}
\newcommand{\hbInCLSrandom}[1]{W_{\text{r}}(#1)}
\newcommand{\hbOptInCLS}[1]{\hbOpt{W}(#1)}
\newcommand{\hbDIntCLS}[2]{I({#1 \to #2})}
%\newcommand{\hbIntCLS}[2]{I(#1, #2)}
\newcommand{\hbIntCLS}[2]{I(#1 \leftrightarrow #2)}
\newcommand{\hbPartition}[1]{\mathbb{#1}} % partition P
\newcommand{\hbPartitionBest}[1]{\overline{\hbPartition{P}_{#1}}} % best partition Pwith K-blocks
%\newcommand{\hbPartitionBest}[1]{\hbPartition{P}_{#1}^{*}} % best partition Pwith K-blocks
\newcommand{\hbMBase}{Base Model}
\newcommand{\hbMA}{Model-A}
\newcommand{\hbMB}{Model-B}
\newcommand{\hbMAB}{Models~A and B}
\newcommand{\hbMC}{Model-C}

\newcommand{\hbIC}[2]{I( #1 \leftrightarrow #2 )}

% ======= specific ===============

\begin{document}
\title[Parent Oriented Teacher Selection Causes Language Diversity]{
	Response to Reviewers\\
	~\\
	~\\
	{\footnotesize
		``Parent Oriented Teacher Selection Causes Language Diversity''\\
		version Dated Feb 20, 2017
	}
}
\author{Ibrahim Cimentepe}
\author{Haluk O. Bingol}
%\affiliation{
%	Department of Computer Engineering\\
%	Bogazici University, Istanbul \\
%	%\today 
%}

\date{\today}
%\date{\hbTimeStamp}

\maketitle

% ======================
\section{Introduction}

We would like to thank our anonymous reviewers 
for pointing out corrections, suggesting ideas and references.
They were very useful and help us to improve readability of the manuscript.

% =======================================
\subsection{Organization}

This response to reviewer is organized as follows.
Individual points are listed under the corresponding reviewers.
Common points that are raised by multiple reviewers 
are addressed in  \refsec{sec:CommonPoints} \hbRoRCommonPoints.

% =======================================
\subsection{Markup in the manuscript}

Changes in the manuscript are highlighted and marked with section number of points.
For example,
changes related to the point
``How $k$-means adapted to language'', 
which is in section 2.2.1,
is marked with 2.2.1.

% =======================================
\subsection{Conventions}

\newcommand{\hbMSample}{\hbMRef{Introduction}}

In order to distinguish 
%
(i)~comments of the reviewers, 
%
(ii)~responses given to the comments, 
%
(iii)~references to the manuscript, and 
%
(iv)~changes done in the manuscript, 
some format, font and color combinations are used.

\begin{hbReviewer}
	This is a sample of comments of reviewer.
	Quotes of the comments of reviewer are given in this format.
\end{hbReviewer}

This is a sample response to the points raised by the reviewer.
During the response, 
one needs to refer to a figure in the manuscript by 
\hbMreffig{3a}.
A section title in the manuscript can be given as \hbMSample.

\begin{hbChanged}
	This is a sample of changes done.
	If one needs to quote the changes done in the manuscript,
	they are given in this format.
\end{hbChanged}

% ======================
\section{Report to the Reviewer \#1}

% =======================================
\subsection{General}
\begin{hbReviewer}
	The authors consider an existing model that describes how language could
	evolve when transferred from one generation to another and extended it
	to the setting in which each offspring learns their language from a particular
	individual who is either geographically or language-wise close to the parent
	of that offspring. They find that such an extended model can promote
	emergence of several subcommunities that share a language, as opposed to
	a global community sharing a universal language.

	I like the idea of the work. Such an extension seems natural and the findings
	are interesting. The paper is well structured and once the reader gets used to
	omnipresent typos it reads quite smoothly. I have three major comments
	and several minor suggestions that I list below (page X,line Y):
\end{hbReviewer}

Thanks.

% =======================================
\subsection{Major Points}

% =======================================
\subsubsection{How $k$-means adapted to language}
\begin{hbReviewer}
	p3,l74:
	I very much like the idea of using the k-means clustering algorithm but
	I'd like to see in more detail how it is adapted to the language domain 
	(possibly in an Appendix).
	For example, as far as I know, in the traditional k-means algorithm,
	at some point one takes the ``centers'' of each current cluster.
	I don't see how this is done in the adaptation 
	which renders the findings of the paper irreproducible. 
\end{hbReviewer}

We agree that our $k$-means adaptation to language domain 
is not given properly.
As suggested, an \hbMAppendix\ is added. 
First $k$-means description in $\mathbb{R}^{D}$ is given.
Then adaptation of $k$-means to language domain is described. 
How to handle ``centers''  in the domain of language is disguised in detail.

% =======================================
\subsubsection{Clusters vs language communities}
\label{sec:ClustersLanguageCommunities}
\begin{hbReviewer}
	p4,l11:
	While I agree that defining average within community comprehension and
	taking K that maximizes it is the most natural thing to do, I'd like to see some
	discussion of why such clusters should correspond to language communities 
	 (as in p7,l25).
	For example, in principle it might happen that 
	 the people with worst mutual understanding
	are all lumped together into one cluster, even though, logically, 
	 they are not a single
	language community.
	(This might be checkable by looking at minimum 
	 within community comprehension.)
\end{hbReviewer}

Thanks for pointing this important issue.
%By definition, $k$-means algorithm is forced to organize $K$ clusters.
%If the nature of the data set is not agree with the selected value of $K$,
%the clusters would not make sense.
%%It is very possible that $k$-means points clusters 
%%that are not well suited to language communities.
%That is, 
%it may group agents that do not ``speak'' the same language in a cluster.
%
%This issue is addressed in different sections.
%
The concept of inter-community comprehension is introduced in
section \hbMOptimumLanguageClusters\ and 
\hbMreffig{2b} is given and  discussed in \hbMSubcommunities.\\
Please see \refsec{sec:diversity} for details.

Potential problems of $k$-means algorithm are discussed in the \hbMAppendix.

%One potential source of problem, 
%that comes with $k$-means algorithm,
%is the selection of $K$ not suitable to the data set.
%Our adaptation carries the same weaknesses.
%This is addressed in different sections.
%(i)~Section \hbMOptimumLanguageClusters\ discusses 
%finding the ``best'' $K$ for the data set and 
%why clusters are expected to be language communities.
%%
%(ii)~In the section on \hbMFutureWork, 
%some discussion on this problem is added, too.
%%
%(iii)~Potential problems of $k$-means algorithm are discussed in the \hbMAppendix.

% =======================================
\subsubsection{``Kˆ* is independent of .. N''}
\begin{hbReviewer}
	p6,l58:
	I don't quite agree with the (bold) statement  "K\^{}* is independent of .. N".
	In Figure 3, the red data points (N=50) seem to be mostly above the green ones (N=100),
	which seem to be in turn mostly above the blue and purple ones (N=150,200).
	To me, that seems like a dependence on N, although a weak one.
	I'd suggest putting the statement more mildly.
\end{hbReviewer}

%\newcommand{\hbMAB}{Models~A and B}
%\newcommand{\hbOpt}[1]{{#1}^*}

We agree that the statement
``We conclude that for \hbMAB,
the optimum community count $\hbOpt{K}$ is 
independent of the size of the population $N$'' 
is difficult to justify. 
The discussion of \hbMreffig{3} in \hbMNumberOfSubcommunities\ is revised  accordingly.
Now it reads:
\begin{hbChanged}
	(ii)~There is a weak relation between $K^{*}$ and $N$.
	For each model, 
	the value of $K^{*}$ is slightly less for larger values of $N$.
\end{hbChanged}

% =======================================
\subsubsection{Gamma values}
	\label{sec:AGammaValues}
\begin{hbReviewer}
	On a related note, what is gamma, empirically, for N=50, 100, 150, 200?
\end{hbReviewer}

For $\gamma$ values, please see \refsec{sec:R2PowerLaw} in \hbRoRCommonPoints.

% =======================================
\subsection{Minor Points}

% =======================================
\subsubsection{p3,l12:}
\begin{hbReviewer}
	p3,l12:
	I suggest "Language evolves \_both\_ through .. \_and\_ as .."
\end{hbReviewer}

Thanks for the correction. It is done.
Now, in \hbMLearningModel, it reads:
\begin{hbChanged}
	Language evolves
	both through agents interacting with each other within a  generation, 
	and as it is transferred from one generation to the next by means of learning.
\end{hbChanged}

% =======================================
\subsubsection{p4,l5:}
\begin{hbReviewer}
	p4,l5:
	This sentence might be misleading. 
	I believe the selected partition is not necessarily the optimal one but 
	the one found by the algorithm 
	(which is, I agree, probably reasonably close to the optimal one). 
	I suggest putting the sentence more mildly.
\end{hbReviewer}

It is true that $k$-means may not provide the optimum partition but near optimum is expected. 
The wording in \hbMOptimumLanguageClusters\
is changed accordingly.
Now it reads:
\begin{hbChanged}
	For a given $K$,
	$k$-means algorithm provides partition
	$\hbPartitionBest{K}$,
	which is expected to be close to the partition with
	the maximum 
	average within community comprehension.
\end{hbChanged}

% =======================================
\subsubsection{p5,l4:}
\begin{hbReviewer}
	p5,l4:
	Parameters M, S, Q are set to some specific values. 
	Is there anything to be said about the dependence on them?
\end{hbReviewer}

In principle parameters $M$, $S$, $Q$ are independent and
can be selected in any way.
For example, Ref~\cite{nowak1999JTB} uses $M = S = 5$ and $Q = 1, 4, 7, 10$.
%Ref~\cite{nowak2000evolution} uses $M = S = 4$ and $M = S = $
Ref~\cite{nowak1999PNAS} uses $M = 20 < S = 40$.

We prefer to report the case, 
where there are more symbols than meanings.
i.e. $M < S$ .
We used the values $M = 8 < S = 15$ and $Q = 4$.
We also investigate $(5,5), (5,8), (8,5)$ and $(8,8)$ values for $(M, S)$.
Different sampling sizes $Q = 1, 4, 7, 10$ are tested.
We found that the quality of language is low for Q = 1, 
whereas it gets higher and 
stays approximately the same for Q = 4, 7 and 10. 
Therefore Q = 4 seems to be the reasonable selection in our simulation.
As previously reported, 
$Q = 1$ slows down learning since it is too little sampling to learn from teacher.

Since there is not much to say, no change is made in the manuscript.

% =======================================
\subsubsection{p5,l5:}
\begin{hbReviewer}
	p5,l5:
	What are the association matrices of the first generation?
\end{hbReviewer}

You are right that this points is missing. 
\hbMModel\ section is changed accordingly.
Now it reads:
\begin{hbChanged}
	The system starts with the first generation,
	whose  association matrices are randomly filled.
	Remaining generations fill their association matrices by learning.
	Every agent $i$ makes exactly one child $i'$.
	The association matrix of a child is initially empty.
	Each child learns her language from her \emph{teacher},
	donated by $t_{i}$.
\end{hbChanged}

% =======================================
\subsubsection{p6,l51:}
\begin{hbReviewer}
	p6,l51: 
	The word "implies" sounds too strong to me, I'd consider "suggests" or 
	the elsewhere frequent "indicates".
\end{hbReviewer}

Thanks for the correction.
``Implies'' is replaced by ``suggests'' in \hbMNumberOfSubcommunities.
Now it reads:
	\begin{hbChanged}
	The shape of the curve in 
	Fig.~2c %\reffig{fig:FigKStar100}
	suggests a power law relation between $\hbOpt{K}$ and $r$, 
	that is,
\end{hbChanged}

% =======================================
\subsubsection{Highlights:}
\begin{hbReviewer}
	I suggest 
	"ones talk" $->$ "someone who talks", 
	"ones that are" $->$ "someone who is", 
	"effects" $->$ "affects"
\end{hbReviewer}

Thanks for the corrections. They are done.

%% ======================
%\newpage

% ======================
\section{Report to the Reviewer \#2}

%================================================
\subsection{General}
\begin{hbReviewer}
	This work extends a previous mathematical model 
	to study language learning from parents to offspring, 
	and studies two types of strategies to select teachers to communicate. 
	It is shown that the two types of strategies induce language diversity 
	after iterated learning across generations of learners. 
	It also finds a power-law relation between the optimal comprehension level 
	and the size of imitation set for selecting teachers. 
	The mathematical parts of the model are solid, 
	and the results are convincing (though see below). 
	It is a topic suitable for JTB. 
	However, there are several concerns 
	that need to be addressed before this simple work can be published. 
\end{hbReviewer}

Thanks.

% =======================================
\subsection{Gong \& Shuai 2012 Proceeding B}
\begin{hbReviewer}
	First, in the background part, 
	the authors only reviewed previous mathematical models 
	from Nowak's group 
	and briefly mentioned some behavioral models of iterated learning 
	and similar laboratory experiments. 
	However, the idea of learning to people 
	that have high comprehension score during cross-generational learning 
	has been implemented in some behavioral models, 
	such as Gong \& Shuai 2012 Proceeding B. 
	In that work, cultural transmission (selection) is based on 
	individuals' linguistic understandability. 
	This work should be mentioned, 
	since the idea of the current paper is not new. 
\end{hbReviewer}

Thank for pointing out this missing reference.
\hbMIntroduction\ is revised accordingly.
Now it reads:
\begin{hbChanged}
	Yet another group consider language 
	as a means to transfer meanings between individuals
	through signaling structures~[8-10].
	%~\cite{%
	%	nowak2002computational,
	%	gong2012coevolution,
	%	kirby2007innateness}.''
\end{hbChanged}
where Ref~[9] is Gong and Shuai 2012.

% =======================================
\subsection{Comprehension scores of both models are already above 0.125}
\begin{hbReviewer}
	Second, in the result part, there are some confusing points. 
	For example, on page 5, above "Subcommunities", the authors said: 
	"In Fig. 1, comprehensions of both Models A and B are
	 below the threshold of $W_{r}(\mathcal{P}) = 0.125$ for $r < 0.05$". 
	However, it is quite clear in that Fig. 1, 
	except under a small $r < 0.05$, 
	comprehension scores of both models are already above 0.125. 
	Please specify this.
\end{hbReviewer}

We agree that wording was not good.
It is changed accordingly in \hbMResultsAndDiscussion.
Now it reads:
\begin{hbChanged}
	In 
	Fig.~1, %\reffig{fig:FigWP.eps},
	comprehensions of both \hbMAB\ are below 
	the threshold of $\hbInCLSrandom{\hbSet{P}} = 0.125$ 
	for $r < 0.05$.
	The comprehensions increase slowly and reach to the level of \hbMC\ 
	as $r$ approaches to $0.5$.
\end{hbChanged}

% =======================================
\subsection{Diversity}
\label{sec:diversity}
\begin{hbReviewer}
	In addition, since the authors talk about "diversity", 
	only showing within community comprehension score is insufficient, 
	you need to also show comprehension score between communities, 
	in this way, people can really have a sense that the system is diverge! 
	Showing the average comprehension score of all communities is also 
	not enough, 
	because it is possible that the low average score is simply 
	due to low score of some community, 
	and between communities, comprehension score is still high; 
	in other words, every community is trying to develop the common language, 
	but some communities are delayed, 
	so the average score of all communities is not high. 
	This is certainly not divergent! 
\end{hbReviewer}

%This was the most challenging point.
We agree that our presentation was focused on within community comprehension.
We have revised the material and 
included discussion of inter-community comprehension, too.
Inter-community comprehension 
$\hbIntCLS{\hbSet{C}_{\alpha}}{\hbSet{C}_{\beta}}$ 
and 
average inter-community comprehension 
$I({\hbPartition{P}_{K}})$
are defined in \hbMOptimumLanguageClusters.
As suggested, 
average inter-community comprehension are given in \hbMreffig{2b} and discussed in \hbMSubcommunities.

Please also see \refsec{sec:ClustersLanguageCommunities}.

% =======================================
\subsection{Single teacher}
\label{sec:singleTeacher}
\begin{hbReviewer}
	Furthermore, the setting that each child only learns from a single parent 
	throughout the learning process is not realistic at all. 
	Teachers should be chosen proportionally 
	and there must be more than one learning cycle. 
	This actually introduces some noise, 
	because in this process, some individual from the imitation set 
	having low comprehension score can still be chosen, 
	which may delay or even reverse the divergence process. 
	Since most parts of the model are already based on probabilities, 
	the learning part should also be like this, 
	simply by setting more than one learning cycle for each child 
	and let teachers in those cycles be chosen probabilistically. 
\end{hbReviewer}

We agree that having single teacher is too much abstraction but an effective one.
Effects of having many teachers can be investigated as 
it is stated in the \hbMFutureWork\ section.
But we feel that it is not in the scope of this paper.
Now it reads:
\begin{hbChanged}
	For example,
	evolution of language can be perceived as a cultural process
	where some group of people is responsible for the transfer.
	That is, more than one teacher could be assigned to each child.
\end{hbChanged}

% =======================================
\subsection{Power law}
	\label{sec:BPowerLaw}

\begin{hbReviewer}
	Finally, in order to show that the relation between K and r is power-law, 
	why not draw Fig. 3 in a log-log scale to see 
	if there are straight lines or not. In addition, 
	some more discussion on this point is needed. 
\end{hbReviewer}

Please see \refsec{sec:R2PowerLaw} in \hbRoRCommonPoints.

% =======================================
\subsection{Cross-generational cultural transmission}
\begin{hbReviewer}
	Third, in the future work, 
	it would be interesting to further study 
	if grandparent grandchild interactions can help keep language 
	from divergence. 
	This can be simply implemented by keeping the grandparent's status 
	and let child have a chance to learning from them, 
	following exactly the same setting for him/her to learn 
	from parent generation. 
	Some early work like 
	Gong \& Shuai 2015 book chapter: 
	Simulating the effects of cross-generational cultural transmission 
	on language change 
	has addressed this based on a behavioral model. 
	A mathematical model like the one in the current paper 
	may complement the findings. 
\end{hbReviewer}

We agree that,
although it is interesting,
we do not consider the impact of grandparents and their generation in this work.
Probably one should consider this together with 
multi-teacher case of \refsec{sec:singleTeacher} as a future study.
We update the \hbMFutureWork\ section. 
It states the possibility of teachers from the generation of grandparents.
Now it reads:
\begin{hbChanged}
	Once many teachers case is considered,
	one may also consider teachers not only from the parent's generation but 
	the generation of grandparents, too~[20].
%	~\cite{%
%		gong2016CrossGenerational}.
\end{hbChanged}
where Ref~[20] is Gong and Shuai 2015.

% =======================================
\subsection{Some tiny points:}
\begin{hbReviewer}
Some tiny points:

1) page 7, right column, line 6: "effect" should be "affect"

2) page 7, right column, line 14: "which we communicate" should be "whom we communicate"
\end{hbReviewer}

Thanks for the corrections. They are done.

% ======================
\section{Common Points}
	\label{sec:CommonPoints}

Common points that are raised by both reviewers are addressed here.

% =======================================
\subsection{Power law discussion}
\label{sec:R2PowerLaw}

Issues related to power law are raised in 
\refsec{sec:AGammaValues} 
and 
\refsec{sec:BPowerLaw}.

Section \hbMNumberOfSubcommunities\ in the manuscript is modified to enhance power law discussion. 
Now \hbMreffig{3}\ has the same values in both linear-linear and log-log scale.
Discussion of straight-line patterns in log-log plot is included 
in \hbMNumberOfSubcommunities.
$\gamma$ values of Model-A and Model-B for various $N$ 
can be seen in \reffig{fig:Gamma}.
These values are given as \hbMreftbl{1} in the manuscript.

% +++++++++++++++++++++++++++++++++++++++
%:-fig gamma
\begin{figure}[!thbp]
	\centering 
	\includegraphics[width=\columnwidth]%
		{Fig-IStar}
	\caption{
		$\gamma$ values of Model-A and Model-B for various $N$.
	} % \caption
	\label{fig:Gamma}
\end{figure}
% +++++++++++++++++++++++++++++++++++++++

% ========================================
\bibliographystyle{ieeetr}
\bibliography{bingol-template-paper}

\end{document}

### 2021-04-01 bingol-template-paper/bingol-template-paper.tex
renaming
student directory modified
midterm is added. Macro library is updated.

--- 2017-11-05 bingol-LaTeX-Template-Paper/Bingol-Template-Paper.tex
@@
 
-%\documentclass[pre,twocolumn,showkeys,longbibliography,nofootinbib]{revtex4-1}
-\documentclass[pre,twocolumn,showkeys,longbibliography]{revtex4-1}
-%\documentclass[twocolumn,preprintnumbers,amsmath,amssymb,superscriptaddress,pre]{revtex4}
+\documentclass[10pt,journal,compsoc]{IEEEtran}
 
-%: ==== HB Header Common Packages v20160423 ====V
-	\usepackage[utf8]{inputenc} % To use Unicode characters
+%: ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ V HB Packages v2021-04-01
+	\usepackage[utf8]{inputenc} 
 	\usepackage[iso]{datetime}
-	%	\usepackage{etex}
+	\newcommand{\hbTimeStamp}{{\color{red}--Draft-- v\today/\currenttime}} % version
+	\usepackage{amssymb}
+	\usepackage{enumerate}
 
@@
 	% magenta, olive, orange, pink, purple, red, teal, violet, white, yellow
+		\definecolor{darkred}{rgb}{0.8,0.1,0.1}
+		\definecolor{darkgreen}{rgb}{0,0.5,0}
+		\definecolor{darkblue}{rgb}{0,0,0.5}
+		\colorlet{RED}{red}
+
 	\usepackage[colorlinks=true,linkcolor=red,urlcolor=blue,citecolor=red]%
@@
 %	\usepackage{subfigure}
-%\usepackage{subfig}
+%	\usepackage{subfig}
 	\usepackage{subcaption}
+% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ A
 
-%: ==== HB Header Common Declarations v20170816 ====V
-	\newcommand{\hbTimeStamp}{{\color{red}--Draft-- v\today/\currenttime}} % version
-	%
+%: ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ V HB Declarations v2021-04-01
 	\newcommand{\reffig}[1]{Fig.~\ref{#1}}
@@
 	\newcommand{\refcite}[1]{Ref~\cite{#1}}
-	\newcommand{\refalg}[1]{Algorithm~\cite{#1}}
+	\newcommand{\refalg}[1]{Algorithm~\ref{#1}}
 	\newcommand{\reflst}[1]{List.~\ref{#1}}  % code listing
@@
 	%
-	\newcommand{\hbQuote}[1]{{\small \textsf{``#1''}}}
+	\newcommand{\hQuote}[1]{{\small \textsf{``#1''}}}
+	\newcommand{\hCode}[1]{\texttt{#1}}
+	\newcommand{\hIdea}[1]{{\color{olive}{\scriptsize [{#1}]}}}
+	\newcommand{\hFootnote}[2]{\footnote{{\color{red} @#1 : }#2}}
+% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ A
+
+%: ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ V HB Math v2021-04-01
+	\usepackage{amsmath, amssymb,amsfonts,amsthm}
 	%
-	\newcommand{\hbCode}[1]{\texttt{#1}}
-	%
-	\newcommand{\hbIdea}[1]{{\color{olive}{\scriptsize [{#1}]}}}
-	\newcommand{\hbFootnote}[2]{\footnote{{\color{red} @#1 : }#2}}
-% ==== HB Header Common Declarations ====A
-
-%: ==== HB Header Common Math v20170530 ====V
-	% ams
-	\usepackage{amsmath, amssymb,amsfonts,amsthm}
-
-	\newcommand{\hbVec}[1]{\mathbf{#1}}	% vector
-	\newcommand{\hbAbs}[1]{| #1 |}	% absolute value
-	\newcommand{\hbNorm}[1]{\left\lVert #1 \right\rVert}	% norm 2
-	\newcommand{\hbMat}[1]{\mathbf{#1}}	% matrix
-	\newcommand{\hbSet}[1]{\mathcal{#1}}	%
-	\newcommand{\argmin}[2]{\underset{#1}{\operatorname{arg \, min}}\;#2}
-	\newcommand{\argmax}[2]{\underset{#1}{\operatorname{arg \, max}}\;#2}
-
-	\theoremstyle{plain}% default
+	\theoremstyle{plain}
 	\newtheorem{thm}{Theorem}[section]
@@
 	\newtheorem*{note}{Note}
-% ==== HB Header Common Math v20170530 ====A
+	%
+	\newcommand{\hDefined}[1]{\textcolor{darkred}{\textit{#1}}}	
+	\newcommand{\hVec}[1]{\mathbf{#1}}	 
+	\newcommand{\hAbs}[1]{\ensuremath{\left \lvert \, #1 \, \right \rvert} } % |x|
+	\newcommand{\hMat}[1]{\mathbf{#1}}
+	\newcommand{\hArgmin}[2]{\underset{#1}{\operatorname{arg \, min}}\;#2}
+	\newcommand{\hArgmax}[2]{\underset{#1}{\operatorname{arg \, max}}\;#2}
+% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ A
 
-%: == HB Code Listing v20161002 ====V
-\usepackage{listingsutf8}
-%\usepackage{listings}             % Include the listings-package
-\definecolor{hbGreen}{rgb}{0,0.6,0}
-\definecolor{hbGray}{rgb}{0.5,0.5,0.5}
-\definecolor{hbMauve}{rgb}{0.58,0,0.82}
-\definecolor{hbbgColor}{rgb}{0.98,0.98,0.98}
-%
-\lstset{ %
-	backgroundcolor=\color{hbbgColor},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}
-%  basicstyle=\tiny, % the size of the fonts that are used for the code
-	basicstyle=\tiny\ttfamily, % the size of the fonts that are used for the code
-%  basicstyle=\scriptsize\ttfamily, % the size of the fonts that are used for the code
-%  basicstyle=\footnotesize\ttfamily, % the size of the fonts that are used for the code
-	breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
-	breaklines=true,                 % sets automatic line breaking
-	captionpos=b,                    % sets the caption-position to bottom
-	commentstyle=\color{hbGreen},    % comment style
-	deletekeywords={...},            % if you want to delete keywords from the given language
-	escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
-	extendedchars=true,              % lets you use non-ASCII characters; for 8-bits encodings only, does not work with UTF-8
-	frame=single,                    % adds a frame around the code
-	keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
-	keywordstyle=\color{blue},       % keyword style
-	language=Sh,                     % the language of the code
-	morekeywords={*,...},            % if you want to add more keywords to the set
-	numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
-	numbersep=5pt,                   % how far the line-numbers are from the code
-	numberstyle=\tiny\color{hbGray}, % the style that is used for the line-numbers
-	rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
-	showspaces=false,                % show spaces everywhere adding particular underscores; it overrides 'showstringspaces'
-	showstringspaces=false,          % underline spaces within strings only
-	showtabs=false,                  % show tabs within strings adding particular underscores
-	stepnumber=2,                    % the step between two line-numbers. If it's 1, each line will be numbered
-	stringstyle=\color{hbMauve},     % string literal style
-	tabsize=1,                       % sets default tabsize to 2 spaces
-	title=\lstname                   % show the filename of files included with \lstinputlisting; also try caption instead of title
-	literate={├}{|}1 {─}{--}1 {└}{+}1
+\hyphenation{
+	op-tical net-works semi-conduc-tor
 }
-\lstset{basicstyle=\ttfamily}
-% == HB Code Listing v20161002 ====A
 
-%: ==== HB Track Changes v20170522 ====V
-	\usepackage{changes}
-	% black, blue, brown, cyan, darkgray, gray, green, lightgray, lime, 
-	% magenta, olive, orange, pink, purple, red, teal, violet, white, yellow
-
-	\definechangesauthor[name=Haluk Bingol,color=purple]{hb}
-	\definechangesauthor[name=Aaaa Bbbb,color=blue]{ab}
-	\setremarkmarkup{(#2)}
-
-	%\listofchanges    % track changes use at the bottom
-
-	% ==== usage
-
-	%\added[id=hb]{
-	%	aaa
-	%}
-
-	%\replaced[id=hb]{
-	%	aaa
-	%}{
-	%	bob
-	%}
-
-	%\deleted[id=hb]{
-	%	aaa
-	%}
-
-	%\added[id=hb]{newText}
-	%\added[id=hb,remark={yourRemark}]{newText}
-	%\deleted[id=hb]{deletedText}
-	%\deleted[id=hb,remark=yourRemark]{deletedText}
-	%\replaced[id=hb]{newText}{deletedText}
-%  ==== HB Track Changes v20170522 ====V
-
-%: ======= specific ===============
-% frequently used terms
-\newcommand{\hbDTex}{\hbCode{.tex}}
-\newcommand{\hbDPdf}{\hbCode{.pdf}}
-\newcommand{\hbSSpecific}{\hbCode{specific}}
-
-\DeclareGraphicsExtensions{.png}
-%
-\DeclareMathOperator{\sgn}{sgn}
-\DeclareMathOperator{\cov}{cov}
-%
-%\newcommand{\hbAvg}[1]{\widehat{#1}}
-\newcommand{\hbOpt}[1]{{#1}^*}
-
-\newcommand{\hSoX}{\mathbb{X}} % generic set
-\newcommand{\hSoN}{\mathbb{N}} % the set of natural numbers
-\newcommand{\hSoR}{\mathbb{R}} % the set of real numbers
-
-% ======= specific ===============
-
-%\usepackage{lineno,hyperref}
-%\modulolinenumbers[5]
-
-%\usepackage{lineno}
-%\usepackage[switch,columnwise]{lineno}
-\RequirePackage{lineno}
-%\linenumbers
-
-% ========================================
+% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ V
 \begin{document}
 
-%\setpagewiselinenumbers
-%\modulolinenumbers[5]
-%\linenumbers
+\title{
+	Title of the paper
+}
 
-\title{
-	My \LaTeX\ Paper Template 
+\author{
+	YourName~Lastname,
+	Haluk~O.~Bingol
+	\IEEEcompsocitemizethanks{
+		\IEEEcompsocthanksitem Y. Lastname and H. O. Bingol  are with Bogazici University.
+	}%
+%	\thanks{
+%		Manuscript received April 19, 2005; 
+%		revised August 26, 2015.
+%	}%
 }
-\author{Haluk O. Bingol}
 
-\affiliation{
-	Deptment of Computer Engineering,\\
-	Bogazici University\\
-	Istanbul, Turkey\\
-	bingol@boun.edu.tr
+\markboth{
+	\hbTimeStamp
+}%
+{
+	\hbTimeStamp
 }
-%\date{\today}
-\date{\hbTimeStamp}
 
+\IEEEtitleabstractindextext{%
 	\begin{abstract}
-	This is my \LaTeX\ template for paper.
+		The abstract goes here.
 	\end{abstract}
 
-% ========================================
-\keywords{
-	LateX paper template;
-	keywordB;
-	keywordC;
+	\begin{IEEEkeywords}
+		KeywordA, keywordB.
+	\end{IEEEkeywords}
 }
 
-% ========================================
 \maketitle
-\tableofcontents
+% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ A
 
-%\linenumbers
-
-% ========================================
+% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
 \section{Introduction}
 
-This is my paper template. 
-It is developed by experience, necessities, best practices.
+Aaa.
 
-% =======================================
-\section{\LaTeX\ source code conventions}
+% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+\subsection{A few reminders}
 
-Consider \LaTeX\ code as programming language code. 
-Actually it is a programming language.
+It would be better if you clone git repository 
+\href
+	{https://github.com/halukbingol/LaTeX-Templates}
+	{https://github.com/halukbingol/LaTeX-Templates}.
+Frequently pull to get updates.
 
-% =======================================
-\subsection{left start}
+Please compile and read 
+\href
+	{https://github.com/halukbingol/LaTeX-Templates/tree/master/bingol-MyLaTeXBestPractices}
+	{MyLaTeXBestPractices} 
+in this repo first.
 
-Start your line at the left most position.
-Do not indent paragraphs unless they are nested within a structure such as \verb!begin-end! block.
-So indentation should be used properly.
+% +++++++++++++++++++++++++++++++++++++++ V
+%: -Fig.
+\begin{figure}[htbp]
+\begin{center}
+	\includegraphics[width=\columnwidth]
+		{Fig-FigureA}
+	\caption{Household layer.}
+	\label{fig:figureA}
+\end{center}
+\end{figure}
+% +++++++++++++++++++++++++++++++++++++++ A
 
-% =======================================
-\subsection{Keep the line length short}
+% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+\section{Related work}
 
-Some editors organize one paragraph of \LaTeX\ code as one line.
-Try not to use such an editors.
-The lines should be short.
-There are two advantages for shorter lines.
-\begin{enumerate}
+Aaa.
 
-	\item
-	\LaTeX\ works on line.
-	Any error message it produces provide you a line number. 
-	If the line is a long one,
-	it is harder to locate the error.
+% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+\section{Our model/method}
 
-	\item
-	Many version control system such as git works on line as prime object.
-	Any change in a line is tracked.
-	If the line is too long,
-	tracking gets more space since entire line has to be considered.
+Aaa
+\begin{align}
+	x = y
+	\label{eq:bbb}
+\end{align}
+bbb.
 
-\end{enumerate}
-If line gets too long,
-divide it by a ``return'' at a proper point.
-A possible places to break the line are ``that'', ``where'', ``which'' phrases or ``else'' part of ``if''.
+% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+\section{Finding/Discussion}
 
-% =======================================
-\subsection{Usage of space and indentation}
+Aaa.
 
-Use space and indentation freely so that your source code would be easy to read and maintain.
-For example use 4 empty line and followed by a comment before section separators.
-See the source code of this paragraph.
-See also the source code of the previous ``enumerate'' block.
+% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
+\section{Conclusion}
 
-In math mode, 
-use spaces to increase readablility.
-For example, see the source code of this in line math equation.
-This is binomial number
-$
-	a = {n \choose r}
-$
-with smart usage of spaces.
-The similar smart space usage can be seen in this math display format, too.
-\begin{align}
-	\bar{a} 
-		= 
-			\frac{1}{\hbAbs{A}}
-			\sum_{i \in A} a_{i}
-		= 5.
-\end{align}
+Aaa.
 
-Using math and not math mode.
-If you are talking about a variable,
-use math mode such as $a$.
-Any numeric value is recommended to be in math mode.
-Notice that -1 in text mode is quite different than $-1$ in math mode.
-Use $k$-means, rather than $k-$means.
+\section*{Acknowledgment}
 
-% =======================================
-\section{Header Part}
+The authors would like to thank Aaaa.
+%
+This work is partially supported by 
+the Turkish Directorate of Strategy and Budget
+under the TAM Project number 2007K12-873.
 
-Note that timestamp \hbTimeStamp\ that helps to keep track of versions while the paper is developed.
-Do not forget to remove it before submission.
-
-% =======================================
-\subsection{TexShop Specific}
-
-I use TexShop.
-It has some features that I use.
-\begin{itemize}
-
-	\item
-	Tag list feature of TeXShop enables you to directly go to a segment of your document.
-	Sections are automatically listed in here.
-	I need to extend that for my purposes.
-	A \LaTeX\  comment starts with ``\hbCode{\%}''.
-	If comment starts with`` \hbCode{\%:}'',
-	note the additional ``\hbCode{:}'',
-	then it is listed in the tags list, too.
-	I use this feature to fast access to some parts of the document such as figures and tables.
-	So I add comments such as 
-	``\hbCode{\%: -fig.1}'' for figure 1 and
-	``\hbCode{\%: -tbl 3}'' for table 3.
-
-	\item 
-	\hbCode{\% !TEX spellcheck = en\_US} forces the spellchecker to use American English.
-
-\end{itemize}
-
-% =======================================
-\subsection{Common Packages}
-
-% =======================================
-\subsection{Common Declarations}
-
-% =======================================
-\subsection{Specific}
-
-Anything that is specific to this paper should be defined in \hbSSpecific\ in the header.
-
-% =======================================
-\section{Multi-Author Case}
-
-Usually more than one author involved.
-They have to keep track of changes, leave messages to each other
-while the paper developes.
-
-Suppose we have two authors, namely HB and AB.
-Note that you need to modify 
-\hbCode{definechangesauthor}
-in 
-\hbCode{changes} package.
-You may want to set different colors, too.
-
-% =======================================
-\subsection{Track Changes}
-
-Authors should be able to add, delete and change parts of the document.
-\deleted[id=hb]{
-	HB removes this part.
-}
-\added[id=ab]{
-	AB adds this part.
-}
-HB wants to replace some part with some others as
-\replaced[id=hb]{
-	the new text
-}{
-	the old text
-}
-
-% =======================================
-\subsection{Communicate with Footnotes}
-
-Another way to communicate between authors is to use of footnotes
-\hbFootnote{HB}{
-	This is a footnote by HB.
-}.
-The other author has another footnote
-\hbFootnote{AB}{
-	This is a footnote by AB.
-}
-.
-Note that this is not the same as regular footnotes that you intent to keep in your final document such as~\footnote{
-	This is a footnote that should stay in the final version of the document.
-}.
-These communication footnotes should be removed at the end of development process.
-Color of ``@HB'' at the start of the footnote should warn you, if you are looking the \hbDPdf\ file online.
-One final search in the \hbDTex\ file for ``@'' should help you to locate unremoved ones.
-
-% =======================================
-\subsection{Lists}
-
-This is an enumeration.
-\begin{enumerate}
-
-	\item 
-	\textbf{Aaaa.}
-	Describe Aaaa.
-
-	\item 
-	\textbf{Aaaa.}
-	Describe Aaaa.
-
-\end{enumerate}
-
-% ========================================
-\section{Math}
-
-Please note the usage of spaces while writing math in \hbDTex\ file.
-Proper usage of space will improve readability of your \LaTeX\ code.
-
-This is math in line. 
-The row sum of $i$ is given as
-$
-	a_{k \cdot} = \sum_{j=1}^{N} a_{i j}
-$,
-where $A = [a_{i j}]$ is a matrix.
-
-If you want your math in display mode there are two options. 
-If you are not going to refer it again, 
-use \verb!\[ ... \]!, 
-which produces
-\[
-	e_{\mu x} 
-	= \frac{a_{\mu x}}{\sum_{x'=1}^{S} a_{\mu x'}},
-	\quad
-	d_{x \mu} 
-	= \frac{a_{\mu x}}{\sum_{\mu'=1}^{M} a_{\mu'x}}.
-\]
-If you are going to refer it again, 
-use \verb!\begin{align} ... \end{align}! to obtain
-\begin{align}
-	a_{ij} =
-		\frac{1}{M}
-		\sum_{\mu = 1}^{M} 
-		{\sum_{x = 1}^{S} 
-			e_{\mu x}^{(i)}
-			d_{x \mu}^{(j)} }.
-	\label{eq:aij}
-\end{align}
-If you have multiple line derivation,
-then \hbCode{align} with \verb!&! is the solution.
-\begin{align}
-	a 
-	&= bbbbb\\
-	&= cccc\\
-	&= ddd.
-\end{align}
-If you do not refer the equation later,
-get rid off numbers by using 
-\verb!\begin{align*} ... \end{align*}!
-as
-\begin{align*}
-	a 
-	&= bbbbb\\
-	&= cccc\\
-	&= ddd.
-\end{align*}
-
-% =======================================
-\subsection{Referring to an Equation}
-
-Refer an equation \refeq{eq:aij}.
-You can refer to an equation \refeq{eq:kBar} in the appendix, too.
-
-% =======================================
-\subsection{Subscripts and superscripts}
-
-Always use curly brackets when you use subscripts or superscripts 
-even if there is no need due to single symbol.
-For example \verb!a_{i}! is better than \verb!a_i! 
-if you consider
-\verb!a_{ij}! and \verb!a_ij!.
-They produce
-$a_{i}$,
-$a_i$,
-$a_{ij}$, and 
-$a_ij$,
-respectively.
-
-% ========================================
-\subsubsection{Comprehension}
-
-Suppose agent $i$ wants to pass meaning $\mu$ to agent $j$.
-Probability of doing this correctly is
-\[
-	\sum_{x = 1}^{S} 
-		e_{\mu x}^{(i)}
-		d_{x \mu}^{(j)} 
-\]
-where 
-$e_{\mu x}^{(i)}$
-and 
-$d_{x \mu}^{(j)}$
-are encoding of $i$ 
-and decoding of $j$, 
-respectively.
-When we average that over all meanings,
-we obtain \emph{comprehension} from $i$ to $j$, 
-that is
-If we want them to communicate both ways,
-we consider \emph{mutual comprehension}
-\[
-	aaa{\hbSet{C}} = 	
-	\frac{1}{2 {\hbAbs{\hbSet{C}} \choose 2}} 
-	\sum_{i \in \hbSet{C}}
-	\sum_{
-		\substack{
-			j \in \hbSet{C}\\
-			j \neq i
-		}
-	} 
-	{bb{i}{j}}.
-\]
-
-% ========================================
-\subsection{$k$-means Clustering Algorithm}
-
-% =======================================
-\subsubsection{Finding Optimum Language Clusters}
-
-\[
-	Aaaa{K} =
-		\argmax
-			{K}
-			{bbb{\mathbb{P}_{K}}}.
-\]
-
-% ========================================
-\section{Figures}
-
-Refer to a figure as \reffig{fig:FigWP.eps}.
-If you want to refer to a figure with multiple graphs,
-there is a way to refer all at once \reffig{fig:N100},
- or individually \reffig{fig:FigWStar} and \reffig{fig:FigKStar100} as required.
-
-% +++++++++++++++++++++++++++++++++++++++
-%: -fig.1
-\begin{figure}[!tbp]
-	\centering 
-	\includegraphics[width=\columnwidth]%
-		{FigIStar.eps}
-	\caption{
-		Single figure.
-	} 
-	% \caption
-	\label{fig:FigWP.eps}
-\end{figure}
-% +++++++++++++++++++++++++++++++++++++++
-
-% +++++++++++++++++++++++++++++++++++++++
-%: -fig 2
-\begin{figure}[!tbp]
-	\begin{subfigure}{\columnwidth}%
-		\includegraphics[width=\columnwidth]
-			{FigWStar.eps}
-		\caption{Within Community Comprehensions} 
-		\label{fig:FigWStar}
-	\end{subfigure}
-	\begin{subfigure}{\columnwidth}%
-		\includegraphics[width=\columnwidth]
-			{FigIStar.eps}
-		\caption{Inter-Community Comprehensions} 
-		\label{fig:FigIStar}
-	\end{subfigure}
-	\begin{subfigure}{\columnwidth}%
-		\includegraphics[width=\columnwidth]
-			{FigKStar100.eps}
-		\caption{Subcommunity Counts} 
-		\label{fig:FigKStar100}
-	\end{subfigure}
-	\caption{
-		Language subcommunities.
-		$N = 100$.
-	} % \caption
-	\label{fig:N100}
-\end{figure}
-% +++++++++++++++++++++++++++++++++++++++
-
-% ========================================
-\section{References and citations}
-\label{sec:ReferencesAndCitations}
-
-Journals may have different ways to present references. 
-If one use consistently the same macro for references,
-simple change in the macro definition can solve 
-the problem of adjusting from one journal to another.
-There are a number of objects such as 
-definitions \refdef{def:PositiveIntegerPowers}, 
-examples \refexmp{exp:Generic},
-figures, 
-code listings \reflst{lst:QuickStart}
- that you can refer to.
-
-% ========================================
-\begin{defn}[Positive Integer Powers]
-	For all $x \in \hSoX$, and $n \in \hSoN$
-	\[
-		x^{n} \triangleq
-		\begin{cases}
-			1, 
-			 &n = 0, \\
-			x, 
-			 &n = 1, \\
-			x x^{n-1},
-			 &n > 1.
-		\end{cases}
-	\]
-	\label{def:PositiveIntegerPowers}
-\end{defn}
-
-% ========================================
-\begin{exmp}
-	\label{exp:Generic}
-	Note that $\hSoX$ is defined in a very generic way.
-	We can take $\hSoX$ as 
-	natural numbers $\hSoN$,
-	real numbers $\hSoR$, or
-	$N \times N$ real matrices $\hSoR_{N \times N}$.
-\end{exmp}
-
-% ========================================
-\lstinputlisting[language=java,basicstyle=\tiny\ttfamily,label=lst:QuickStart,caption=Node object]
-	{code-sample.java}
-
-% ========================================
-\subsection{References}
-
-Any object that will be referred,
-should have a label declaration such as
-\verb!\label{A:B}!,
-where 
-$A$ is type indicator and
-$B$ is unique label with in the type.
-Commonly used type indicator are given in \reftbl{tbl:TypeIndicators}.
-See ``HB Header Common Declarations'' in the source for more.
-
-% +++++++++++++++++++++++++++++++++++++++
-%: -table TypeIndicators
-\begin{table}[th]
-	\caption{Reference type indicators}
-	\begin{center}
-	\begin{tabular}{|l |l |l |l |}
-		\hline
-		Type
-		&Indicator
-		&Code
-		&Result\\
-		\hline
-		%
-		Equation
-		&eq
-		&\verb!\refeq!
-		&\refeq{aaa}\\
-		%
-		Figure
-		&fig
-		&\verb!\reffig!
-		&\reffig{aaa}\\
-		%
-		Table
-		&tbl
-		&\verb!\reftbl!
-		&\reftbl{aa}\\
-		%
-		Section
-		&sec
-		&\verb!\refsec!
-		&\refsec{aa}\\
-		%
-		Citation
-		&-
-		&\verb!\refcite!
-		&\refcite{aa}\\
-		%
-		Definition
-		&def
-		&\verb!\refdef!
-		&\refdef{aaa}\\
-		%
-		Theorem
-		&thm
-		&\verb!\refthm!
-		&\refthm{aa}\\
-		%
-		Algorithm
-		&alg
-		&\verb!\refalg!
-		&\refalg{aaa}\\
-		%
-		List
-		&lst
-		&\verb!\reflst!
-		&\reflst{aa}\\
-		%
-		aaa
-		&aaa
-		&\verb!aaaa!
-		&aaa\\
-		\hline
-	\end{tabular}
-	\end{center}
-	\label{tbl:TypeIndicators}
-\end{table}%
-% +++++++++++++++++++++++++++++++++++++++
-
-It is possible to refer a number of objects within \LaTeX.
-Refer an equation \refeq{eq:aij}, which can be obtained by \verb!\refeq{eq:aij}!. 
-A figure can be referred by means of \verb!\reffig{fig:N100}!, which produces \reffig{fig:N100}.
-Similarly a table can be referred by \reftbl{tbl:gamma} by using \verb!\reftbl{tbl:gamma}!.
-A section can be referred by \refsec{sec:ReferencesAndCitations}, 
-that is, 
-\verb!\refsec{sec:ReferencesAndCitations}!.
-
-% ========================================
-\subsection{Citations}
-
-Check the source to see how I prefer to cite~\cite{%
-	duda2012pattern,
-	mackay2003information,
-	theodoridis2010patternMatlab}.
-In this way, you can see the citations easily both in .tex and .pdf forms.
-In .pdf file, citations are in color.
-If you want to modify,
-see 
-\hbCode{linkcolor=red}
-in 
-\hbCode{hyperref}.
-Use citation at  the end of sentence as much as possible.
-Connect citation to the word with tilda as in the case here~\cite{%
-	AAa2017bb}.
-See the code.
-If a sentence starts with citation,
-start with \refcite{%
-	AAa2017bb}  
-not with \cite{%
-	AAa2017bb}.
-
-% =======================================
-\subsection{Tables}
-
-Refer to tables as \reftbl{tbl:gamma}.
-
-% +++++++++++++++++++++++++++++++++++++++
-%: -table 1
-\begin{table}[th]
-	\caption{$\gamma$ values for $r > 0.03$}
-	\begin{center}
-	\begin{tabular}{|r|cc|}
-		\hline
-		$N$
-		&Model-A %\quad
-		&Model-B\\
-		\hline
-		%
-		50
-		&0.72
-		&0.62\\
-		%
-		100
-		&0.69
-		&0.63\\
-		%
-		150
-		&0.72
-		&0.69\\
-		%
-		200
-		&0.68
-		&0.72\\
-		\hline
-	\end{tabular}
-	\end{center}
-	\label{tbl:gamma}
-\end{table}%
-% +++++++++++++++++++++++++++++++++++++++
-
-% =======================================
-\appendix
-%: ==== HB Header Common for Appendix v20170517 ====V
-\newcommand{\hbAppendixPrefix}{A}
-%
-\renewcommand{\thefigure}{\hbAppendixPrefix\arabic{figure}}
-\setcounter{figure}{0}
-\renewcommand{\thetable}{\hbAppendixPrefix\arabic{table}} 
-\setcounter{table}{0}
-\renewcommand{\theequation}{\hbAppendixPrefix\arabic{equation}} 
-\setcounter{equation}{0}
-% ==== HB Header Common for Appendix v20170517 ====A
-
-\section{Appendix}
-\label{sec:appendix}
-
-% =======================================
-\subsection{$k$-means Algorithm}
-	\label{sec:kMeansAlgorithm}
-
-An equation
-\begin{equation}
-	\label{eq:kBar}
-	\bar{k} = \argmin{k} d(\mathbf{x}_{n},  \mathbf{m}_{k}(t-1))
-\end{equation}
-is here.
-
-% =======================================
-\subsection{$k$-means in Language Domain}
-
-%% =======================================
-\section*{Acknowledgments}
-
-%\textbf{Acknowledgments.}
-This work was partially supported 
-by Bogazici University Research Fund [BAP-2008-08A105], 
-by the Turkish State Planning Organization (DPT) TAM Project [2007K120610], 
-and 
-by COST action TD1210.
-
-% ========================================
-\bibliographystyle{ieeetr}
-
-\bibliography{Bingol-Template-Paper}
-
-% =========
-\listofchanges   % track changes use at the bottom
-% =========
+\bibliographystyle{IEEEtran}
+\bibliography{bingol-template-paper}
 

### 2021-05-10 bingol-MyLaTeXBestPractices/code-sample.java
citing web pages.

@@ -1,11 +1,0 @@
-public class Node {
-	String name;
-	String lastName;
-	Node link;
-
-	public Node(){
-		name ="";
-		lastName="";
-		link = null;
-	}
-}
